---
title: "Fear Conditioning- Cue on Day 3"
author: "Kaylee Helfrich"
date: "6/1/2020-2/24/2021"
output:
  pdf_document: default
  html_document: default
data: "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows fear conditioning data from the rat offspring used for behavior testing. This shows only the analysis of the Cue (Day 3) results. The other results are in separate RMarkdown files. The four treatment groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(data.table)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
ActualGroupOrder <- c("CON", "CON+Iron", "PAE", "PAE+Iron")
```
```{r echo = FALSE}
print(data_frame[,c(1:11,25:31)])
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

# Cue Graphs

## Making a data table to graph results from the male cue test- by minute
```{r}
#Cue minute 1 Table
M.Cue.1 <- Males %>% select(Exposure, Cue.1min)
M.Cue.1$Phase <- strrep("1-Minute1", 1)
names(M.Cue.1)[2] <- "Value"

#Cue minute 2 Table
M.Cue.2 <- Males %>% select(Exposure, Cue.2min)
M.Cue.2$Phase <- strrep("2-Minute2", 1)
names(M.Cue.2)[2] <- "Value"

#Cue minute 3 Table
M.Cue.3 <- Males %>% select(Exposure, Cue.3min)
M.Cue.3$Phase <- strrep("3-Minute3", 1)
names(M.Cue.3)[2] <- "Value"

#Cue minute 4 Table
M.Cue.4 <- Males %>% select(Exposure, Cue.4min)
M.Cue.4$Phase <- strrep("4-Minute4", 1)
names(M.Cue.4)[2] <- "Value"

#Cue minute 5 Table
M.Cue.5 <- Males %>% select(Exposure, Cue.5min)
M.Cue.5$Phase <- strrep("5-Minute5", 1)
names(M.Cue.5)[2] <- "Value"

#Combine Tables
Male.cue.minute <- rbind(M.Cue.1, M.Cue.2, M.Cue.3, M.Cue.4, M.Cue.5)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Male.cue.minute <- Male.cue.minute %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the male cue by minute results
```{r}
png("FC_Male_Cue_ByMinute_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Male.cue.minute.plot <- ggplot(Male.cue.minute, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Male Fear Conditioning- Cue") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("1","2", "3", "4", "5")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Male.cue.minute.plot)
dev.off()
```
```{r Male Cue By Minute Box Whisker, echo = FALSE}
print(Male.cue.minute.plot)
```

## Making a data table to graph results from the male cue test- by section
```{r}
#Cue baseline Table
M.Cue.baseline <- Males %>% select(Exposure, Cue.Baseline)
M.Cue.baseline$Phase <- strrep("1-Baseline", 1)
names(M.Cue.baseline)[2] <- "Value"

#Cue cue Table
M.Cue.cue <- Males %>% select(Exposure, Cue.Total)
M.Cue.cue$Phase <- strrep("2-Cue", 1)
names(M.Cue.cue)[2] <- "Value"

#Combine Tables
Male.cue.section <- rbind(M.Cue.baseline, M.Cue.cue)
Male.cue.section <- Male.cue.section %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the male cue by section results
```{r}
png("FC_Male_Cue_BySection_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Male.cue.section.plot <- ggplot(Male.cue.section, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Male Fear Conditioning- Cue") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Portion of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("Baseline","Cue")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Male.cue.section.plot)
dev.off()
```
```{r Male Cue By Section Box Whisker, echo = FALSE}
print(Male.cue.section.plot)
```

## Making a data table to graph results from the female cue test- by minute
```{r}
#Cue minute 1 Table
F.Cue.1 <- Females %>% select(Exposure, Cue.1min)
F.Cue.1$Phase <- strrep("1-Minute1", 1)
names(F.Cue.1)[2] <- "Value"

#Cue minute 2 Table
F.Cue.2 <- Females %>% select(Exposure, Cue.2min)
F.Cue.2$Phase <- strrep("2-Minute2", 1)
names(F.Cue.2)[2] <- "Value"

#Cue minute 3 Table
F.Cue.3 <- Females %>% select(Exposure, Cue.3min)
F.Cue.3$Phase <- strrep("3-Minute3", 1)
names(F.Cue.3)[2] <- "Value"

#Cue minute 4 Table
F.Cue.4 <- Females %>% select(Exposure, Cue.4min)
F.Cue.4$Phase <- strrep("4-Minute4", 1)
names(F.Cue.4)[2] <- "Value"

#Cue minute 5 Table
F.Cue.5 <- Females %>% select(Exposure, Cue.5min)
F.Cue.5$Phase <- strrep("5-Minute5", 1)
names(F.Cue.5)[2] <- "Value"

#Combine Tables
Female.cue.minute <- rbind(F.Cue.1, F.Cue.2, F.Cue.3, F.Cue.4, F.Cue.5)
Female.cue.minute <- Female.cue.minute %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the female cue by minute results
```{r}
png("FC_Female_Cue_ByMinute_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Female.cue.minute.plot <- ggplot(Female.cue.minute, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Female Fear Conditioning- Cue") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("1","2", "3", "4", "5")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Female.cue.minute.plot)
dev.off()
```
```{r Female Cue By Minute Box Whisker, echo = FALSE}
print(Female.cue.minute.plot)
```

## Making a data table to graph results from the female cue test- by section
```{r}
#Cue baseline Table
F.Cue.baseline <- Females %>% select(Exposure, Cue.Baseline)
F.Cue.baseline$Phase <- strrep("1-Baseline", 1)
names(F.Cue.baseline)[2] <- "Value"

#Cue cue Table
F.Cue.cue <- Females %>% select(Exposure, Cue.Total)
F.Cue.cue$Phase <- strrep("2-Cue", 1)
names(F.Cue.cue)[2] <- "Value"

#Combine Tables
Female.cue.section <- rbind(F.Cue.baseline, F.Cue.cue)
Female.cue.section <- Female.cue.section %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the female cue by section results
```{r}
png("FC_Female_Cue_BySection_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Female.cue.section.plot <- ggplot(Female.cue.section, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Female Fear Conditioning- Cue") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Portion of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("Baseline","Cue")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Female.cue.section.plot)
dev.off()
```
```{r Female Cue By Section Box Whisker, echo = FALSE}
print(Female.cue.section.plot)
```

# Cue Bar Graphs

## Male Cue Bar Graphs
## Normalize the number of points in each group to graph the bar graph overlaid with points
```{r}
neworder <- c("CON", "PAE", "CON+Iron", "PAE+Iron")
Males <- Males %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
Groupcount <- Males %>% count(Exposure) 
NumPoints <- max(Groupcount$n) 
DiffFunc <- function(x) NumPoints - x
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) 
DiffPoints$Exposure.Group <- ActualGroupOrder 
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN) 
MD <- DiffPoints[1,1] 
MDFe <- DiffPoints[2,1]
PAE <- DiffPoints[3,1]
PAEFe <- DiffPoints[4,1]

DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 50)) 
vector <- rep(c("CON", "PAE", "CON+Iron", "PAE+Iron"), times = c(MD, PAE, MDFe, PAEFe)) 
DF_extra$Exposure.Group <- vector
DF_extra <- DF_extra[,c(1:4, 51, 5:50)]
DF_extra <- setNames(DF_extra, names(Males))
DF_extra$Sex <- c("M")
Males <- rbind(Males, DF_extra)
print(Males %>% count(Exposure))
Males <- Males[order(Males$Exposure), ]

MSex_NumPoints <- NumPoints
```

## Making a data table to graph results from the male Cue test- total freezing
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(Males$Cue.Total, as.character(Males$Exposure), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = MSex_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = MSex_NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(Males$Cue.Total, as.character(Males$Exposure), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = MSex_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = MSex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, Males$Cue.Total) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine <- dataframe_combine %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)

#Make Graph#
png("Males_FC_TotalCue_PAExFe_Bar&Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Male FC- Total Freezing During Cue") +
  ylab(expression("% Time Freezing")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 24, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Male FC Cue Bargraph, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

## Female Cue Bar Graphs
## Normalize the number of points in each group to graph the bar graph overlaid with points
```{r}
neworder <- c("CON", "PAE", "CON+Iron", "PAE+Iron")
Females <- Females %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
Groupcount <- Females %>% count(Exposure) 
NumPoints <- max(Groupcount$n) 
DiffFunc <- function(x) NumPoints - x
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) 
DiffPoints$Exposure.Group <- ActualGroupOrder 
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN) 
MD <- DiffPoints[1,1] 
MDFe <- DiffPoints[2,1]
PAE <- DiffPoints[3,1]
PAEFe <- DiffPoints[4,1]

DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 50)) 
vector <- rep(c("CON", "PAE", "CON+Iron", "PAE+Iron"), times = c(MD, PAE, MDFe, PAEFe)) 
DF_extra$Exposure.Group <- vector
DF_extra <- DF_extra[,c(1:4, 51, 5:50)]
DF_extra <- setNames(DF_extra, names(Females))
DF_extra$Sex <- c("M")
Females <- rbind(Females, DF_extra)
print(Females %>% count(Exposure))
Females <- Females[order(Females$Exposure), ]

FSex_NumPoints <- NumPoints
```

## Making a data table to graph results from the Female Cue test- total freezing
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(Females$Cue.Total, as.character(Females$Exposure), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = FSex_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = FSex_NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(Females$Cue.Total, as.character(Females$Exposure), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = FSex_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = FSex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, Females$Cue.Total) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine <- dataframe_combine %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)

#Make Graph#
png("Females_FC_TotalCue_PAExFe_Bar&Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Female FC- Total Freezing During Cue") +
  ylab(expression("% Time Freezing")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 24, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black",family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Female FC Cue Bargraph, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Remake Cue Graphs to be Bar Graphs
## Males Cue Bar Graphs
```{r}
#Create new column to distinguish the groups
Male.cue.minute$Group <- paste(Male.cue.minute$Exposure, Male.cue.minute$Phase, sep="_")
#Calcuate the mean for each group- exposure and test stage
MC.table <-aggregate(Male.cue.minute[, 2], list(Male.cue.minute$Group), mean, na.rm = TRUE)
MC.vector <- as.vector(MC.table$Group.1)
```

### Males Cue- Equalize Row Number by Exposure
```{r}
Groupcount <- Male.cue.minute %>% count(Group) 
NumPoints <- max(Groupcount$n)
DiffFunc <- function(x) NumPoints - x 
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) 
DiffPoints$Group <- MC.vector
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN)
MD <- DiffPoints[1,1]
MDIron <- DiffPoints[6,1]
PAE <- DiffPoints[11,1]
PAEIron <- DiffPoints[16,1]
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 3))
vector <- rep(c("MD_1-Minute1", "MD_2-Minute2", "MD_3-Minute3", "MD_4-Minute4", "MD_5-Minute5", "MD+Iron_1-Minute1", "MD+Iron_2-Minute2", "MD+Iron_3-Minute3", "MD+Iron_4-Minute4", "MD+Iron_5-Minute5", "PAE_1-Minute1", "PAE_2-Minute2", "PAE_3-Minute3", "PAE_4-Minute4", "PAE_5-Minute5", "PAE+Iron_1-Minute1", "PAE+Iron_2-Minute2", "PAE+Iron_3-Minute3", "PAE+Iron_4-Minute4", "PAE+Iron_5-Minute5"), times = c(MD, MD, MD, MD, MD, MDIron, MDIron, MDIron, MDIron, MDIron, PAE, PAE, PAE, PAE, PAE, PAEIron, PAEIron, PAEIron, PAEIron, PAEIron))
DF_extra$Group <- vector
DF_extra <- setNames(DF_extra, names(Male.cue.minute))
MC_new <- rbind(Male.cue.minute, DF_extra)
print(MC_new %>% count(Group))
MC_new <- MC_new[order(MC_new$Group), ]
Male_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Male Graphs
```{r echo = FALSE}
print(Nrow)
```

## Males Bar Graph of Cue
This graph does not contain individual dots, since they did not work with the more complicated graph. If the individual points are required, then the plots for Minute 1, Minute 2, Total Freezing, etc. will have to be made separately.
```{r warning = FALSE, message = FALSE}
Mean <- tapply(MC_new$Value, as.character(MC_new$Group), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Group <- rep(MC.vector, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(MC_new$Value, as.character(MC_new$Group), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Group <- rep(MC.vector, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, MC_new$Value, MC_new$Exposure, MC_new$Phase) #change column
colnames(dataframe_combine)[5] <- "Value"
colnames(dataframe_combine)[6] <- "Exposure"
colnames(dataframe_combine)[7] <- "Phase"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FC_Male_Cue_AllData_PAExFe_Bargraph.png", units="in", width=12, height=7, res=600) 

XLabels <- c("Minute 1", "Minute 2", "Minute 3", "Minute 4", "Minute 5")

p <- ggplot(data=subset(dataframe_combine, !is.na(Value)), aes(fill=Exposure, y=Mean, x=Phase, na.rm = TRUE)) + 
    geom_bar(position="dodge", stat="identity", color="black") +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Mean, ymax=Upper), width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,110)) +
  ggtitle("Males FC- Cue") +
  ylab(expression("% Time Freezing")) + 
   theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        #legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
print(p)
dev.off() 
```
```{r Male Cue Barplot, echo = FALSE}
print(p)
```

## Females Cue Bar Graphs
```{r}
#Create new column to distinguish the groups
Female.cue.minute$Group <- paste(Female.cue.minute$Exposure, Female.cue.minute$Phase, sep="_")
#Calcuate the mean for each group- exposure and test stage
MC.table <-aggregate(Female.cue.minute[, 2], list(Female.cue.minute$Group), mean, na.rm = TRUE)
MC.vector <- as.vector(MC.table$Group.1)
```

### Females Cue- Equalize Row Number by Exposure
```{r}
Groupcount <- Female.cue.minute %>% count(Group) 
NumPoints <- max(Groupcount$n)
DiffFunc <- function(x) NumPoints - x 
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) 
DiffPoints$Group <- MC.vector
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN)
MD <- DiffPoints[1,1]
MDIron <- DiffPoints[6,1]
PAE <- DiffPoints[11,1]
PAEIron <- DiffPoints[16,1]
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 3))
vector <- rep(c("MD_1-Minute1", "MD_2-Minute2", "MD_3-Minute3", "MD_4-Minute4", "MD_5-Minute5", "MD+Iron_1-Minute1", "MD+Iron_2-Minute2", "MD+Iron_3-Minute3", "MD+Iron_4-Minute4", "MD+Iron_5-Minute5", "PAE_1-Minute1", "PAE_2-Minute2", "PAE_3-Minute3", "PAE_4-Minute4", "PAE_5-Minute5", "PAE+Iron_1-Minute1", "PAE+Iron_2-Minute2", "PAE+Iron_3-Minute3", "PAE+Iron_4-Minute4", "PAE+Iron_5-Minute5"), times = c(MD, MD, MD, MD, MD, MDIron, MDIron, MDIron, MDIron, MDIron, PAE, PAE, PAE, PAE, PAE, PAEIron, PAEIron, PAEIron, PAEIron, PAEIron))
DF_extra$Group <- vector
DF_extra <- setNames(DF_extra, names(Female.cue.minute))
MC_new <- rbind(Female.cue.minute, DF_extra)
print(MC_new %>% count(Group))
MC_new <- MC_new[order(MC_new$Group), ]
Female_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Female Graphs
```{r echo = FALSE}
print(Nrow)
```

## Females Bar Graph of Cue
This graph does not contain individual dots, since they did not work with the more complicated graph. If the individual points are required, then the plots for Minute 1, Minute 2, Total Freezing, etc. will have to be made separately.
```{r warning = FALSE, message = FALSE}
Mean <- tapply(MC_new$Value, as.character(MC_new$Group), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Group <- rep(MC.vector, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(MC_new$Value, as.character(MC_new$Group), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Group <- rep(MC.vector, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, MC_new$Value, MC_new$Exposure, MC_new$Phase) #change column
colnames(dataframe_combine)[5] <- "Value"
colnames(dataframe_combine)[6] <- "Exposure"
colnames(dataframe_combine)[7] <- "Phase"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FC_Female_Cue_AllData_PAExFe_Bargraph.png", units="in", width=12, height=7, res=600) 

XLabels <- c("Minute 1", "Minute 2", "Minute 3", "Minute 4", "Minute 5")

p <- ggplot(data=subset(dataframe_combine, !is.na(Value)), aes(fill=Exposure, y=Mean, x=Phase, na.rm = TRUE)) + 
    geom_bar(position="dodge", stat="identity", color="black") +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Mean, ymax=Upper), width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,110)) +
  ggtitle("Females FC- Cue") +
  ylab(expression("% Time Freezing")) + 
   theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        #legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
print(p)
dev.off() 
```
```{r Female Cue Barplot, echo = FALSE}
print(p)
```

# Create line graphs for the Cue sessions

## Males
```{r}
#Minute 1
Males.1 <- tapply(Males$Cue.1min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.1 <- as.data.frame(Males.1)
Males.1$Exposure <- ActualGroupOrder
colnames(Males.1)[1] <- "Mean" #fix column name
Males.sterr.1 <- tapply(Males$Cue.1min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.1$Sterr <- Males.sterr.1
Males.1$Minute <- rep("1", 4)

#Minute 2
Males.2 <- tapply(Males$Cue.2min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.2 <- as.data.frame(Males.2)
Males.2$Exposure <- ActualGroupOrder
colnames(Males.2)[1] <- "Mean" #fix column name
Males.sterr.2 <- tapply(Males$Cue.2min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.2$Sterr <- Males.sterr.2
Males.2$Minute <- rep("2", 4)

#Minute 3
Males.3 <- tapply(Males$Cue.3min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.3 <- as.data.frame(Males.3)
Males.3$Exposure <- ActualGroupOrder
colnames(Males.3)[1] <- "Mean" #fix column name
Males.sterr.3 <- tapply(Males$Cue.3min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.3$Sterr <- Males.sterr.3
Males.3$Minute <- rep("3", 4)

#Minute 4
Males.4 <- tapply(Males$Cue.4min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.4 <- as.data.frame(Males.4)
Males.4$Exposure <- ActualGroupOrder
colnames(Males.4)[1] <- "Mean" #fix column name
Males.sterr.4 <- tapply(Males$Cue.4min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.4$Sterr <- Males.sterr.4
Males.4$Minute <- rep("4", 4)

#Minute 5
Males.5 <- tapply(Males$Cue.5min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.5 <- as.data.frame(Males.5)
Males.5$Exposure <- ActualGroupOrder
colnames(Males.5)[1] <- "Mean" #fix column name
Males.sterr.5 <- tapply(Males$Cue.5min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.5$Sterr <- Males.sterr.5
Males.5$Minute <- rep("5", 4)

#Merge all tables
Males_combined <- rbind(Males.1, Males.2, Males.3, Males.4, Males.5)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
names(Males_combined)[1] <- "Exposure"

#Create error bar data
Males_combined$Upper <- Males_combined$Mean + Males_combined$Sterr
Males_combined$Lower <- Males_combined$Mean - Males_combined$Sterr

Males_combined <- Males_combined %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Graph Male Cue Results as a Linegraph
```{r}
png("FC_Males_Cue_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

XLabels2 <- c("1", "2", "3", "4", "5")

males.graph <- ggplot(data=Males_combined, aes(x=Minute, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Male FC Cue") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Experiment")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(males.graph)
dev.off() 
```
```{r Male FC Cue Line Graph, echo = FALSE}
print(males.graph)
```

## Females
```{r}
#Minute 1
Females.1 <- tapply(Females$Cue.1min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.1 <- as.data.frame(Females.1)
Females.1$Exposure <- ActualGroupOrder
colnames(Females.1)[1] <- "Mean" #fix column name
Females.sterr.1 <- tapply(Females$Cue.1min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.1$Sterr <- Females.sterr.1
Females.1$Minute <- rep("1", 4)

#Minute 2
Females.2 <- tapply(Females$Cue.2min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.2 <- as.data.frame(Females.2)
Females.2$Exposure <- ActualGroupOrder
colnames(Females.2)[1] <- "Mean" #fix column name
Females.sterr.2 <- tapply(Females$Cue.2min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.2$Sterr <- Females.sterr.2
Females.2$Minute <- rep("2", 4)

#Minute 3
Females.3 <- tapply(Females$Cue.3min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.3 <- as.data.frame(Females.3)
Females.3$Exposure <- ActualGroupOrder
colnames(Females.3)[1] <- "Mean" #fix column name
Females.sterr.3 <- tapply(Females$Cue.3min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.3$Sterr <- Females.sterr.3
Females.3$Minute <- rep("3", 4)

#Minute 4
Females.4 <- tapply(Females$Cue.4min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.4 <- as.data.frame(Females.4)
Females.4$Exposure <- ActualGroupOrder
colnames(Females.4)[1] <- "Mean" #fix column name
Females.sterr.4 <- tapply(Females$Cue.4min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.4$Sterr <- Females.sterr.4
Females.4$Minute <- rep("4", 4)

#Minute 5
Females.5 <- tapply(Females$Cue.5min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.5 <- as.data.frame(Females.5)
Females.5$Exposure <- ActualGroupOrder
colnames(Females.5)[1] <- "Mean" #fix column name
Females.sterr.5 <- tapply(Females$Cue.5min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.5$Sterr <- Females.sterr.5
Females.5$Minute <- rep("5", 4)

#Merge all tables
Females_combined <- rbind(Females.1, Females.2, Females.3, Females.4, Females.5)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
names(Females_combined)[1] <- "Exposure"

#Create error bar data
Females_combined$Upper <- Females_combined$Mean + Females_combined$Sterr
Females_combined$Lower <- Females_combined$Mean - Females_combined$Sterr

Females_combined <- Females_combined %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Graph Female Cue Results as a Linegraph
```{r}
png("FC_Females_Cue_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

XLabels2 <- c("1", "2", "3", "4", "5")

Females.graph <- ggplot(data=Females_combined, aes(x=Minute, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Females FC Cue") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Experiment")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(Females.graph)
dev.off() 
```
```{r Female FC Cue Line Graph, echo = FALSE}
print(Females.graph)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```