---
title: "Fear Conditioning- Conditioning on Day 1"
author: "Kaylee Helfrich"
date: "6/1/2020-2/23/2021"
output:
  pdf_document: default
  html_document: default
data: "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
opts_chunk$set(tidy = F)
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows fear conditioning data from the rat offspring used for behavior testing. This shows only the analysis of the Conditioning (Day 1) results. The other results are in separate RMarkdown files. The four treatment groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(data.table)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
ActualGroupOrder <- c("MD", "MD+Iron", "PAE", "PAE+Iron")
```
```{r echo = FALSE}
print(data_frame[,1:18])
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

# Conditioning Graphs

## Making a data table to graph results from the male conditioning test
```{r}
#Baseline Table
M.Cond.Baseline <- Males %>% select(Exposure, Conditioning.Baseline)
M.Cond.Baseline$Phase <- strrep("1-Baseline", 1)
names(M.Cond.Baseline)[2] <- "Value"

#CSUS1 Table
M.Cond.CSUS1 <- Males %>% select(Exposure, Conditioning.CSUS1)
M.Cond.CSUS1$Phase <- strrep("2-CSUS1", 1)
names(M.Cond.CSUS1)[2] <- "Value"

#CSUS2 Table
M.Cond.CSUS2 <- Males %>% select(Exposure, Conditioning.CSUS2)
M.Cond.CSUS2$Phase <- strrep("3-CSUS2", 1)
names(M.Cond.CSUS2)[2] <- "Value"

#CS3 Table
M.Cond.CS3 <- Males %>% select(Exposure, Conditioning.CS3)
M.Cond.CS3$Phase <- strrep("4-CS3", 1)
names(M.Cond.CS3)[2] <- "Value"

#End Table
#M.Cond.End <- Males %>% select(Exposure.Group, Conditioning.End)
#M.Cond.End$Phase <- strrep("5-End", 1)
#names(M.Cond.End)[2] <- "Value"

#Combine Tables and set order of exposure groups to MD, PAE, MD+Iron, and PAE+Iron instead of alphabetical
Male.conditioning <- rbind(M.Cond.Baseline, M.Cond.CSUS1, M.Cond.CSUS2, M.Cond.CS3)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Male.conditioning <- Male.conditioning %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the male conditioning results
```{r}
png("FC_Male_Conditioning_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Male.conditioning.plot <- ggplot(Male.conditioning, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Male FC- Conditioning") +
  ylab(expression("% Time Freezing")) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("Baseline","CSUS1","CSUS2", "CS3", "End")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_blank(),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Male.conditioning.plot)
dev.off()
```
```{r Male Conditioning Box Whisker, echo = FALSE}
print(Male.conditioning.plot)
```

## Making a data table to graph results from the female conditioning test
```{r}
#Baseline Table
F.Cond.Baseline <- Females %>% select(Exposure, Conditioning.Baseline)
F.Cond.Baseline$Phase <- strrep("1-Baseline", 1)
names(F.Cond.Baseline)[2] <- "Value"

#CSUS1 Table
F.Cond.CSUS1 <- Females %>% select(Exposure, Conditioning.CSUS1)
F.Cond.CSUS1$Phase <- strrep("2-CSUS1", 1)
names(F.Cond.CSUS1)[2] <- "Value"

#CSUS2 Table
F.Cond.CSUS2 <- Females %>% select(Exposure, Conditioning.CSUS2)
F.Cond.CSUS2$Phase <- strrep("3-CSUS2", 1)
names(F.Cond.CSUS2)[2] <- "Value"

#CS3 Table
F.Cond.CS3 <- Females %>% select(Exposure, Conditioning.CS3)
F.Cond.CS3$Phase <- strrep("4-CS3", 1)
names(F.Cond.CS3)[2] <- "Value"

#End Table
#F.Cond.End <- Females %>% select(Exposure, Conditioning.End)
#F.Cond.End$Phase <- strrep("5-End", 1)
#names(F.Cond.End)[2] <- "Value"

#Combine Tables and set order of exposure groups to MD, PAE, MD+Iron, and PAE+Iron instead of alphabetical
Female.conditioning <- rbind(F.Cond.Baseline, F.Cond.CSUS1, F.Cond.CSUS2, F.Cond.CS3)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Female.conditioning <- Female.conditioning %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the female conditioning results
```{r}
png("FC_Female_Conditioning_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Female.conditioning.plot <- ggplot(Female.conditioning, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Female FC- Conditioning") +
  ylab(expression("% Time Freezing")) + 
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("Baseline","CSUS1","CSUS2", "CS3", "End")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_blank(),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Female.conditioning.plot)
dev.off()
```
```{r Female Conditioning Box Whisker, echo = FALSE}
print(Female.conditioning.plot)
```

# Remake Conditioning Graphs to be Bar Graphs
```{r}
#Create new column to distinguish the groups
Male.conditioning$Group <- paste(Male.conditioning$Exposure, Male.conditioning$Phase, sep="_")
#Calcuate the mean for each group- exposure and test stage
MC.table <-aggregate(Male.conditioning[, 2], list(Male.conditioning$Group), mean, na.rm = TRUE)
MC.vector <- as.vector(MC.table$Group.1)
```

### Males Conditioning- Equalize Row Number by Exposure
```{r}
Groupcount <- Male.conditioning %>% count(Group) 
NumPoints <- max(Groupcount$n)
DiffFunc <- function(x) NumPoints - x 
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) 
DiffPoints$Group <- MC.vector
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN)
MD1B <- DiffPoints[1,1]
MD2CSUS1 <- DiffPoints[2,1]
MD3CSUS2 <- DiffPoints[3,1]
MD4CS3 <- DiffPoints[4,1] 
MDIron1B <- DiffPoints[5,1]
MDIron2CSUS1 <- DiffPoints[6,1]
MDIron3CSUS2 <- DiffPoints[7,1]
MDIron4CS3 <- DiffPoints[8,1]
PAE1B <- DiffPoints[9,1]
PAE2CSUS1 <- DiffPoints[10,1]
PAE3CSUS2 <- DiffPoints[11,1]
PAE4CS3 <- DiffPoints[12,1]
PAEIron1B <- DiffPoints[13,1]
PAEIron2CSUS1 <- DiffPoints[14,1]
PAEIron3CSUS2 <- DiffPoints[15,1]
PAEIron4CS3 <- DiffPoints[16,1]

DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 3))
vector <- rep(c("MD_1-Baseline", "MD_2-CSUS1", "MD_3-CSUS2", "MD_4-CS3", "MD+Iron_1-Baseline", "MD+Iron_2-CSUS1", "MD+Iron_3-CSUS2", "MD+Iron_4-CS3", "PAE_1-Baseline", "PAE_2-CSUS1", "PAE_3-CSUS2", "PAE_4-CS3", "PAE+Iron_1-Baseline", "PAE+Iron_2-CSUS1", "PAE+Iron_3-CSUS2", "PAE+Iron_4-CS3"), times = c(MD1B, MD2CSUS1, MD3CSUS2, MD4CS3, MDIron1B, MDIron2CSUS1, MDIron3CSUS2, MDIron4CS3, PAE1B, PAE2CSUS1, PAE3CSUS2, PAE4CS3, PAEIron1B, PAEIron2CSUS1, PAEIron3CSUS2, PAEIron4CS3))
DF_extra$Group <- vector
DF_extra <- setNames(DF_extra, names(Male.conditioning))
MC_new <- rbind(Male.conditioning, DF_extra)
print(MC_new %>% count(Group))
MC_new <- MC_new[order(MC_new$Group), ]
Male_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Male Graphs
```{r echo = FALSE}
print(Nrow)
```

## Males Bar Graph of Conditioning
This graph does not contain individual dots, since they did not work with the more complicated graph. If the individual points are required, then the plots for Baseline, CSUS1, etc. will have to be made separately.
```{r warning = FALSE, message = FALSE}
Mean <- tapply(MC_new$Value, as.character(MC_new$Group), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Group <- rep(MC.vector, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(MC_new$Value, as.character(MC_new$Group), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Group <- rep(MC.vector, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, MC_new$Value, MC_new$Exposure, MC_new$Phase) #change column
colnames(dataframe_combine)[5] <- "Value"
colnames(dataframe_combine)[6] <- "Exposure"
colnames(dataframe_combine)[7] <- "Phase"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FC_Male_Conditioning_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

XLabels <- c("Baseline", "CSUS1", "CSUS2", "CS3")

p <- ggplot(data=subset(dataframe_combine, !is.na(Value)), aes(fill=Exposure, y=Mean, x=Phase, na.rm = TRUE)) + 
    geom_bar(position="dodge", stat="identity", color="black") +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Mean, ymax=Upper), width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,110)) +
  ggtitle("Males FC- Conditioning") +
  ylab(expression("% Time Freezing")) + 
   theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        #legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
print(p)
dev.off() 
```
```{r Male Conditioning Barplot, echo = FALSE}
print(p)
```

## Females remaking graphs
```{r}
#Create new column to distinguish the groups
Female.conditioning$Group <- paste(Female.conditioning$Exposure, Female.conditioning$Phase, sep="_")
#Calcuate the mean for each group- exposure and test stage
FC.table <-aggregate(Female.conditioning[, 2], list(Female.conditioning$Group), mean, na.rm = TRUE)
FC.vector <- as.vector(FC.table$Group.1)
```

### Females Conditioning- Equalize Row Number by Exposure
```{r}
Groupcount <- Female.conditioning %>% count(Group) 
NumPoints <- max(Groupcount$n)
DiffFunc <- function(x) NumPoints - x 
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) 
DiffPoints$Group <- MC.vector
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN)
MD1B <- DiffPoints[1,1]
MD2CSUS1 <- DiffPoints[2,1]
MD3CSUS2 <- DiffPoints[3,1]
MD4CS3 <- DiffPoints[4,1] 
MDIron1B <- DiffPoints[5,1]
MDIron2CSUS1 <- DiffPoints[6,1]
MDIron3CSUS2 <- DiffPoints[7,1]
MDIron4CS3 <- DiffPoints[8,1]
PAE1B <- DiffPoints[9,1]
PAE2CSUS1 <- DiffPoints[10,1]
PAE3CSUS2 <- DiffPoints[11,1]
PAE4CS3 <- DiffPoints[12,1]
PAEIron1B <- DiffPoints[13,1]
PAEIron2CSUS1 <- DiffPoints[14,1]
PAEIron3CSUS2 <- DiffPoints[15,1]
PAEIron4CS3 <- DiffPoints[16,1]

DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 3))
vector <- rep(c("MD_1-Baseline", "MD_2-CSUS1", "MD_3-CSUS2", "MD_4-CS3", "MD+Iron_1-Baseline", "MD+Iron_2-CSUS1", "MD+Iron_3-CSUS2", "MD+Iron_4-CS3", "PAE_1-Baseline", "PAE_2-CSUS1", "PAE_3-CSUS2", "PAE_4-CS3", "PAE+Iron_1-Baseline", "PAE+Iron_2-CSUS1", "PAE+Iron_3-CSUS2", "PAE+Iron_4-CS3"), times = c(MD1B, MD2CSUS1, MD3CSUS2, MD4CS3, MDIron1B, MDIron2CSUS1, MDIron3CSUS2, MDIron4CS3, PAE1B, PAE2CSUS1, PAE3CSUS2, PAE4CS3, PAEIron1B, PAEIron2CSUS1, PAEIron3CSUS2, PAEIron4CS3))
DF_extra$Group <- vector
DF_extra <- setNames(DF_extra, names(Female.conditioning))
FC_new <- rbind(Female.conditioning, DF_extra)
print(FC_new %>% count(Group))
FC_new <- FC_new[order(FC_new$Group), ]
Female_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Female Graphs
```{r echo = FALSE}
print(Nrow)
```

## Females Bar Graph of Conditioning
This graph does not contain individual dots, since they did not work with the more complicated graph. If the individual points are required, then the plots for Baseline, CSUS1, etc. will have to be made separately.
```{r warning = FALSE, message = FALSE}
Mean <- tapply(FC_new$Value, as.character(FC_new$Group), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Group <- rep(FC.vector, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(FC_new$Value, as.character(FC_new$Group), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Group <- rep(FC.vector, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, FC_new$Value, FC_new$Exposure, FC_new$Phase) #change column
colnames(dataframe_combine)[5] <- "Value"
colnames(dataframe_combine)[6] <- "Exposure"
colnames(dataframe_combine)[7] <- "Phase"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FC_Female_Conditioning_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

XLabels <- c("Baseline", "CSUS1", "CSUS2", "CS3")

p <- ggplot(data=subset(dataframe_combine, !is.na(Value)), aes(fill=Exposure, y=Mean, x=Phase, na.rm = TRUE)) + 
    geom_bar(position="dodge", stat="identity", color="black") +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Mean, ymax=Upper), width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,110)) +
  ggtitle("Females FC- Conditioning") +
  ylab(expression("% Time Freezing")) + 
   theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        #legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
print(p)
dev.off() 
```
```{r Female Conditioning Barplot, echo = FALSE}
print(p)
```

# Create line graphs for the conditioning sessions

## Create mean and standard error table for males
```{r}
#Baseline
Males.1 <- tapply(Males$Conditioning.Baseline, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.1 <- as.data.frame(Males.1)
Males.1$Exposure <- ActualGroupOrder
colnames(Males.1)[1] <- "Mean" #fix column name
Males.sterr.1 <- tapply(Males$Conditioning.Baseline, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.1$Sterr <- Males.sterr.1
Males.1$Phase <- rep("1-Baseline", 4)

#CSUS1
Males.2 <- tapply(Males$Conditioning.CSUS1, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.2 <- as.data.frame(Males.2)
Males.2$Exposure <- ActualGroupOrder
colnames(Males.2)[1] <- "Mean" #fix column name
Males.sterr.2 <- tapply(Males$Conditioning.CSUS1, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.2$Sterr <- Males.sterr.2
Males.2$Phase <- rep("2-CSUS1", 4)

#CSUS2
Males.3 <- tapply(Males$Conditioning.CSUS2, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.3 <- as.data.frame(Males.3)
Males.3$Exposure <- ActualGroupOrder
colnames(Males.3)[1] <- "Mean" #fix column name
Males.sterr.3 <- tapply(Males$Conditioning.CSUS2, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.3$Sterr <- Males.sterr.3
Males.3$Phase <- rep("3-CSUS2", 4)

#CS3
Males.4 <- tapply(Males$Conditioning.CS3, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.4 <- as.data.frame(Males.4)
Males.4$Exposure <- ActualGroupOrder
colnames(Males.4)[1] <- "Mean" #fix column name
Males.sterr.4 <- tapply(Males$Conditioning.CS3, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.4$Sterr <- Males.sterr.4
Males.4$Phase <- rep("4-CS3", 4)

#Merge all tables
Males_combined <- rbind(Males.1, Males.2, Males.3, Males.4)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
names(Males_combined)[1] <- "Exposure"

#Create error bar data
Males_combined$Upper <- Males_combined$Mean + Males_combined$Sterr
Males_combined$Lower <- Males_combined$Mean - Males_combined$Sterr
```

## Graph Male Conditioning Results- with Standard Error
```{r}
png("FC_Males_Conditioning_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

XLabels2 <- c("Baseline", "CSUS1", "CSUS2", "CS3")

males.graph <- ggplot(data=Males_combined, aes(x=Phase, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Male FC Conditioning") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Experiment Phase")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(males.graph)
dev.off() 
```
```{r Male FC Conditioning Line Graph, echo = FALSE}
print(males.graph)
```

## Create mean and standard error table for females
```{r}
#Baseline
Females.1 <- tapply(Females$Conditioning.Baseline, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.1 <- as.data.frame(Females.1)
Females.1$Exposure <- ActualGroupOrder
colnames(Females.1)[1] <- "Mean" #fix column name
Females.sterr.1 <- tapply(Females$Conditioning.Baseline, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.1$Sterr <- Females.sterr.1
Females.1$Phase <- rep("1-Baseline", 4)

#CSUS1
Females.2 <- tapply(Females$Conditioning.CSUS1, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.2 <- as.data.frame(Females.2)
Females.2$Exposure <- ActualGroupOrder
colnames(Females.2)[1] <- "Mean" #fix column name
Females.sterr.2 <- tapply(Females$Conditioning.CSUS1, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.2$Sterr <- Females.sterr.2
Females.2$Phase <- rep("2-CSUS1", 4)

#CSUS2
Females.3 <- tapply(Females$Conditioning.CSUS2, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.3 <- as.data.frame(Females.3)
Females.3$Exposure <- ActualGroupOrder
colnames(Females.3)[1] <- "Mean" #fix column name
Females.sterr.3 <- tapply(Females$Conditioning.CSUS2, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.3$Sterr <- Females.sterr.3
Females.3$Phase <- rep("3-CSUS2", 4)

#CS3
Females.4 <- tapply(Females$Conditioning.CS3, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.4 <- as.data.frame(Females.4)
Females.4$Exposure <- ActualGroupOrder
colnames(Females.4)[1] <- "Mean" #fix column name
Females.sterr.4 <- tapply(Females$Conditioning.CS3, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.4$Sterr <- Females.sterr.4
Females.4$Phase <- rep("4-CS3", 4)

#Merge all tables
Females_combined <- rbind(Females.1, Females.2, Females.3, Females.4)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
names(Females_combined)[1] <- "Exposure"

#Create error bar data
Females_combined$Upper <- Females_combined$Mean + Females_combined$Sterr
Females_combined$Lower <- Females_combined$Mean - Females_combined$Sterr
```

## Graph Female Conditioning Results- with Standard Error
```{r}
png("FC_Females_Conditioning_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

XLabels2 <- c("Baseline", "CSUS1", "CSUS2", "CS3")

Females.graph <- ggplot(data=Females_combined, aes(x=Phase, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Female FC Conditioning") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Experiment Phase")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(Females.graph)
dev.off() 
```
```{r Female FC Conditioning Line Graph, echo = FALSE}
print(Females.graph)
```

# Session Information
```{r echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```