---
title: "Fear Conditioning- Context on Day 2"
author: "Kaylee Helfrich"
date: "6/1/2020-2/23/2021"
output:
  pdf_document: default
  html_document: default
data: "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows fear conditioning data from the rat offspring used for behavior testing. This shows only the analysis of the Context (Day 2) results. The other results are in separate RMarkdown files. The four treatment groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(data.table)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
ActualGroupOrder <- c("CON", "CON+Iron", "PAE", "PAE+Iron")
```
```{r echo = FALSE}
print(data_frame[,c(1:11,19:24)])
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

# Context Graphs

## Making a data table to graph results from the male context test
```{r}
#Context minute 1 Table
M.Context.1 <- Males %>% select(Exposure, Context.1min)
M.Context.1$Phase <- strrep("1-Minute1", 1)
names(M.Context.1)[2] <- "Value"

#Context minute 2 Table
M.Context.2 <- Males %>% select(Exposure, Context.2min)
M.Context.2$Phase <- strrep("2-Minute2", 1)
names(M.Context.2)[2] <- "Value"

#Context minute 3 Table
M.Context.3 <- Males %>% select(Exposure, Context.3min)
M.Context.3$Phase <- strrep("3-Minute3", 1)
names(M.Context.3)[2] <- "Value"

#Context minute 4 Table
M.Context.4 <- Males %>% select(Exposure, Context.4min)
M.Context.4$Phase <- strrep("4-Minute4", 1)
names(M.Context.4)[2] <- "Value"

#Context minute 5 Table
M.Context.5 <- Males %>% select(Exposure, Context.5min)
M.Context.5$Phase <- strrep("5-Minute5", 1)
names(M.Context.5)[2] <- "Value"

#Context Total Table
M.Context.Total <- Males %>% select(Exposure, Context.Total)
M.Context.Total$Phase <- strrep("6-Total", 1)
names(M.Context.Total)[2] <- "Value"

#Combine Tables
Male.context <- rbind(M.Context.1, M.Context.2, M.Context.3, M.Context.4, M.Context.5, M.Context.Total)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Male.context <- Male.context %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the male context results
```{r}
png("FC_Male_Context_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Male.context.plot <- ggplot(Male.context, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Male FC- Context") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("1","2", "3", "4", "5", "Total")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Male.context.plot)
dev.off()
```
```{r Male Context Box Whisker, echo = FALSE}
print(Male.context.plot)
```

## Making a data table to graph results from the female context test
```{r}
#Context minute 1 Table
F.Context.1 <- Females %>% select(Exposure, Context.1min)
F.Context.1$Phase <- strrep("1-Minute1", 1)
names(F.Context.1)[2] <- "Value"

#Context minute 2 Table
F.Context.2 <- Females %>% select(Exposure, Context.2min)
F.Context.2$Phase <- strrep("2-Minute2", 1)
names(F.Context.2)[2] <- "Value"

#Context minute 3 Table
F.Context.3 <- Females %>% select(Exposure, Context.3min)
F.Context.3$Phase <- strrep("3-Minute3", 1)
names(F.Context.3)[2] <- "Value"

#Context minute 4 Table
F.Context.4 <- Females %>% select(Exposure, Context.4min)
F.Context.4$Phase <- strrep("4-Minute4", 1)
names(F.Context.4)[2] <- "Value"

#Context minute 5 Table
F.Context.5 <- Females %>% select(Exposure, Context.5min)
F.Context.5$Phase <- strrep("5-Minute5", 1)
names(F.Context.5)[2] <- "Value"

#Context Total Table
F.Context.Total <- Females %>% select(Exposure, Context.Total)
F.Context.Total$Phase <- strrep("6-Total", 1)
names(F.Context.Total)[2] <- "Value"

#Combine Tables
Female.context <- rbind(F.Context.1, F.Context.2, F.Context.3, F.Context.4, F.Context.5, F.Context.Total)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Female.context <- Female.context %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the female context results
```{r}
png("FC_Female_Context_PAExFe_BoxWhisker.png", units="in", width=8, height=6, res=600) 

Female.context.plot <- ggplot(Female.context, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Female FC- Context") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("1","2", "3", "4", "5", "Total")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Female.context.plot)
dev.off()
```
```{r Female Context Box Whisker, echo = FALSE}
print(Female.context.plot)
```

# Context Bar Graphs- Total Freezing

## Male Context Bar Graphs
## Normalize the number of points in each group to graph the bar graph overlaid with points
```{r}
neworder <- c("CON", "PAE", "CON+Iron", "PAE+Iron")
Males <- Males %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
Groupcount <- Males %>% count(Exposure) 
NumPoints <- max(Groupcount$n) 
DiffFunc <- function(x) NumPoints - x
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) 
DiffPoints$Exposure.Group <- ActualGroupOrder 
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN) 
MD <- DiffPoints[1,1] 
MDFe <- DiffPoints[2,1]
PAE <- DiffPoints[3,1]
PAEFe <- DiffPoints[4,1]

DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 50)) 
vector <- rep(c("CON", "PAE", "CON+Iron", "PAE+Iron"), times = c(MD, PAE, MDFe, PAEFe)) 
DF_extra$Exposure.Group <- vector
DF_extra <- DF_extra[,c(1:4, 51, 5:50)]
DF_extra <- setNames(DF_extra, names(Males))
DF_extra$Sex <- c("M")
Males <- rbind(Males, DF_extra)
print(Males %>% count(Exposure))
Males <- Males[order(Males$Exposure), ]

MSex_NumPoints <- NumPoints
```

## Making a data table to graph results from the male context test- total freezing
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(Males$Context.Total, as.character(Males$Exposure), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = MSex_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = MSex_NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(Males$Context.Total, as.character(Males$Exposure), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = MSex_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = MSex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, Males$Context.Total) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine <- dataframe_combine %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)

#Make Graph#
png("Males_FC_TotalContext_PAExFe_Bar&Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Male FC- Total Freezing During Context") +
  ylab(expression("% Time Freezing")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 24, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Male FC Context Bargraph, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

## Female Context Bar Graphs
## Normalize the number of points in each group to graph the bar graph overlaid with points
```{r}
neworder <- c("CON", "PAE", "CON+Iron", "PAE+Iron")
Females <- Females %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
Groupcount <- Females %>% count(Exposure) 
NumPoints <- max(Groupcount$n) 
DiffFunc <- function(x) NumPoints - x
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) 
DiffPoints$Exposure.Group <- ActualGroupOrder 
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN) 
MD <- DiffPoints[1,1] 
MDFe <- DiffPoints[2,1]
PAE <- DiffPoints[3,1]
PAEFe <- DiffPoints[4,1]

DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 50)) 
vector <- rep(c("CON", "PAE", "CON+Iron", "PAE+Iron"), times = c(MD, PAE, MDFe, PAEFe)) 
DF_extra$Exposure.Group <- vector
DF_extra <- DF_extra[,c(1:4, 51, 5:50)]
DF_extra <- setNames(DF_extra, names(Females))
DF_extra$Sex <- c("F")
Females <- rbind(Females, DF_extra)
print(Females %>% count(Exposure))
Females <- Females[order(Females$Exposure), ]

FSex_NumPoints <- NumPoints
```

## Making a data table to graph results from the Female context test- total freezing
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(Females$Context.Total, as.character(Females$Exposure), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = FSex_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = FSex_NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(Females$Context.Total, as.character(Females$Exposure), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = FSex_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = FSex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, Females$Context.Total) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine <- dataframe_combine %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)

#Make Graph#
png("Females_FC_TotalContext_PAExFe_Bar&Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Female FC- Total Freezing During Context") +
  ylab(expression("% Time Freezing")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 24, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Female FC Context Bargraph, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Remake Context Graphs to be Bar Graphs
## Males Context Bar Graphs
```{r}
#Create new column to distinguish the groups
Male.context$Group <- paste(Male.context$Exposure, Male.context$Phase, sep="_")
#Calcuate the mean for each group- exposure and test stage
MC.table <-aggregate(Male.context[, 2], list(Male.context$Group), mean, na.rm = TRUE)
MC.vector <- as.vector(MC.table$Group.1)
```

### Males context- Equalize Row Number by Exposure
```{r}
Groupcount <- Male.context %>% count(Group) 
NumPoints <- max(Groupcount$n)
DiffFunc <- function(x) NumPoints - x 
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) 
DiffPoints$Group <- MC.vector
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN)
MD <- DiffPoints[1,1]
MDIron <- DiffPoints[7,1]
PAE <- DiffPoints[13,1]
PAEIron <- DiffPoints[19,1]
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 3))
vector <- rep(c("MD_1-Minute1", "MD_2-Minute2", "MD_3-Minute3", "MD_4-Minute4", "MD_5-Minute5", "MD_6-Total", "MD+Iron_1-Minute1", "MD+Iron_2-Minute2", "MD+Iron_3-Minute3", "MD+Iron_4-Minute4", "MD+Iron_5-Minute5", "MD+Iron_6-Total", "PAE_1-Minute1", "PAE_2-Minute2", "PAE_3-Minute3", "PAE_4-Minute4", "PAE_5-Minute5", "PAE_6-Total", "PAE+Iron_1-Minute1", "PAE+Iron_2-Minute2", "PAE+Iron_3-Minute3", "PAE+Iron_4-Minute4", "PAE+Iron_5-Minute5", "PAE+Iron_6-Total"), times = c(MD, MD, MD, MD, MD, MD, MDIron, MDIron, MDIron, MDIron, MDIron, MDIron, PAE, PAE, PAE, PAE, PAE, PAE, PAEIron, PAEIron, PAEIron, PAEIron, PAEIron, PAEIron))
DF_extra$Group <- vector
DF_extra <- setNames(DF_extra, names(Male.context))
MC_new <- rbind(Male.context, DF_extra)
print(MC_new %>% count(Group))
MC_new <- MC_new[order(MC_new$Group), ]
Male_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Male Graphs
```{r echo = FALSE}
print(Nrow)
```

## Males Bar Graph of context
This graph does not contain individual dots, since they did not work with the more complicated graph. If the individual points are required, then the plots for Minute 1, Minute 2, Total Freezing, etc. will have to be made separately.
```{r warning = FALSE, message = FALSE}
Mean <- tapply(MC_new$Value, as.character(MC_new$Group), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Group <- rep(MC.vector, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(MC_new$Value, as.character(MC_new$Group), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Group <- rep(MC.vector, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, MC_new$Value, MC_new$Exposure, MC_new$Phase) #change column
colnames(dataframe_combine)[5] <- "Value"
colnames(dataframe_combine)[6] <- "Exposure"
colnames(dataframe_combine)[7] <- "Phase"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FC_Male_context_AllData_PAExFe_Bargraph.png", units="in", width=12, height=7, res=600) 

XLabels <- c("Minute 1", "Minute 2", "Minute 3", "Minute 4", "Minute 5", "Total Freezing")

p <- ggplot(data=subset(dataframe_combine, !is.na(Value)), aes(fill=Exposure, y=Mean, x=Phase, na.rm = TRUE)) + 
    geom_bar(position="dodge", stat="identity", color="black") +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Mean, ymax=Upper), width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,110)) +
  ggtitle("Males FC- context") +
  ylab(expression("% Time Freezing")) + 
   theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        #legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
print(p)
dev.off() 
```
```{r Male context Barplot, echo = FALSE}
print(p)
```

## Females Context Bar Graphs
```{r}
#Create new column to distinguish the groups
Female.context$Group <- paste(Female.context$Exposure, Female.context$Phase, sep="_")
#Calcuate the mean for each group- exposure and test stage
MC.table <-aggregate(Female.context[, 2], list(Female.context$Group), mean, na.rm = TRUE)
MC.vector <- as.vector(MC.table$Group.1)
```

### Females context- Equalize Row Number by Exposure
```{r}
Groupcount <- Female.context %>% count(Group) 
NumPoints <- max(Groupcount$n)
DiffFunc <- function(x) NumPoints - x 
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) 
DiffPoints$Group <- MC.vector
colnames(DiffPoints)[1] <- "NumberN"
Nrow <- sum(DiffPoints$NumberN)
MD <- DiffPoints[1,1]
MDIron <- DiffPoints[7,1]
PAE <- DiffPoints[13,1]
PAEIron <- DiffPoints[19,1]
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 3))
vector <- rep(c("MD_1-Minute1", "MD_2-Minute2", "MD_3-Minute3", "MD_4-Minute4", "MD_5-Minute5", "MD_6-Total", "MD+Iron_1-Minute1", "MD+Iron_2-Minute2", "MD+Iron_3-Minute3", "MD+Iron_4-Minute4", "MD+Iron_5-Minute5", "MD+Iron_6-Total", "PAE_1-Minute1", "PAE_2-Minute2", "PAE_3-Minute3", "PAE_4-Minute4", "PAE_5-Minute5", "PAE_6-Total", "PAE+Iron_1-Minute1", "PAE+Iron_2-Minute2", "PAE+Iron_3-Minute3", "PAE+Iron_4-Minute4", "PAE+Iron_5-Minute5", "PAE+Iron_6-Total"), times = c(MD, MD, MD, MD, MD, MD, MDIron, MDIron, MDIron, MDIron, MDIron, MDIron, PAE, PAE, PAE, PAE, PAE, PAE, PAEIron, PAEIron, PAEIron, PAEIron, PAEIron, PAEIron))
DF_extra$Group <- vector
DF_extra <- setNames(DF_extra, names(Female.context))
MC_new <- rbind(Female.context, DF_extra)
print(MC_new %>% count(Group))
MC_new <- MC_new[order(MC_new$Group), ]
Female_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Female Graphs
```{r echo = FALSE}
print(Nrow)
```

## Females Bar Graph of context
This graph does not contain individual dots, since they did not work with the more complicated graph. If the individual points are required, then the plots for Minute 1, Minute 2, Total Freezing, etc. will have to be made separately.
```{r warning = FALSE, message = FALSE}
Mean <- tapply(MC_new$Value, as.character(MC_new$Group), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Group <- rep(MC.vector, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(MC_new$Value, as.character(MC_new$Group), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Group <- rep(MC.vector, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, MC_new$Value, MC_new$Exposure, MC_new$Phase) #change column
colnames(dataframe_combine)[5] <- "Value"
colnames(dataframe_combine)[6] <- "Exposure"
colnames(dataframe_combine)[7] <- "Phase"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FC_Female_context_AllData_PAExFe_Bargraph.png", units="in", width=12, height=7, res=600) 

XLabels <- c("Minute 1", "Minute 2", "Minute 3", "Minute 4", "Minute 5", "Total Freezing")

p <- ggplot(data=subset(dataframe_combine, !is.na(Value)), aes(fill=Exposure, y=Mean, x=Phase, na.rm = TRUE)) + 
    geom_bar(position="dodge", stat="identity", color="black") +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Mean, ymax=Upper), width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,110)) +
  ggtitle("Females FC- context") +
  ylab(expression("% Time Freezing")) + 
   theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        #legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 0, vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
print(p)
dev.off() 
```
```{r Female context Barplot, echo = FALSE}
print(p)
```

# Create line graphs for the context sessions

## Males
```{r}
#Minute 1
Males.1 <- tapply(Males$Context.1min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.1 <- as.data.frame(Males.1)
Males.1$Exposure <- ActualGroupOrder
colnames(Males.1)[1] <- "Mean" #fix column name
Males.sterr.1 <- tapply(Males$Context.1min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.1$Sterr <- Males.sterr.1
Males.1$Minute <- rep("1", 4)

#Minute 2
Males.2 <- tapply(Males$Context.2min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.2 <- as.data.frame(Males.2)
Males.2$Exposure <- ActualGroupOrder
colnames(Males.2)[1] <- "Mean" #fix column name
Males.sterr.2 <- tapply(Males$Context.2min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.2$Sterr <- Males.sterr.2
Males.2$Minute <- rep("2", 4)

#Minute 3
Males.3 <- tapply(Males$Context.3min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.3 <- as.data.frame(Males.3)
Males.3$Exposure <- ActualGroupOrder
colnames(Males.3)[1] <- "Mean" #fix column name
Males.sterr.3 <- tapply(Males$Context.3min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.3$Sterr <- Males.sterr.3
Males.3$Minute <- rep("3", 4)

#Minute 4
Males.4 <- tapply(Males$Context.4min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.4 <- as.data.frame(Males.4)
Males.4$Exposure <- ActualGroupOrder
colnames(Males.4)[1] <- "Mean" #fix column name
Males.sterr.4 <- tapply(Males$Context.4min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.4$Sterr <- Males.sterr.4
Males.4$Minute <- rep("4", 4)

#Minute 5
Males.5 <- tapply(Males$Context.5min, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.5 <- as.data.frame(Males.5)
Males.5$Exposure <- ActualGroupOrder
colnames(Males.5)[1] <- "Mean" #fix column name
Males.sterr.5 <- tapply(Males$Context.5min, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.5$Sterr <- Males.sterr.5
Males.5$Minute <- rep("5", 4)

#Merge all tables
Males_combined <- rbind(Males.1, Males.2, Males.3, Males.4, Males.5)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
names(Males_combined)[1] <- "Exposure"

#Create error bar data
Males_combined$Upper <- Males_combined$Mean + Males_combined$Sterr
Males_combined$Lower <- Males_combined$Mean - Males_combined$Sterr

Males_combined <- Males_combined %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Graph Male Context Results as a Linegraph
```{r}
png("FC_Males_Context_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

XLabels2 <- c("1", "2", "3", "4", "5")

males.graph <- ggplot(data=Males_combined, aes(x=Minute, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Male FC Context") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Experiment")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(males.graph)
dev.off() 
```
```{r Male FC Context Line Graph, echo = FALSE}
print(males.graph)
```

## Females
```{r}
#Minute 1
Females.1 <- tapply(Females$Context.1min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.1 <- as.data.frame(Females.1)
Females.1$Exposure <- ActualGroupOrder
colnames(Females.1)[1] <- "Mean" #fix column name
Females.sterr.1 <- tapply(Females$Context.1min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.1$Sterr <- Females.sterr.1
Females.1$Minute <- rep("1", 4)

#Minute 2
Females.2 <- tapply(Females$Context.2min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.2 <- as.data.frame(Females.2)
Females.2$Exposure <- ActualGroupOrder
colnames(Females.2)[1] <- "Mean" #fix column name
Females.sterr.2 <- tapply(Females$Context.2min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.2$Sterr <- Females.sterr.2
Females.2$Minute <- rep("2", 4)

#Minute 3
Females.3 <- tapply(Females$Context.3min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.3 <- as.data.frame(Females.3)
Females.3$Exposure <- ActualGroupOrder
colnames(Females.3)[1] <- "Mean" #fix column name
Females.sterr.3 <- tapply(Females$Context.3min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.3$Sterr <- Females.sterr.3
Females.3$Minute <- rep("3", 4)

#Minute 4
Females.4 <- tapply(Females$Context.4min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.4 <- as.data.frame(Females.4)
Females.4$Exposure <- ActualGroupOrder
colnames(Females.4)[1] <- "Mean" #fix column name
Females.sterr.4 <- tapply(Females$Context.4min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.4$Sterr <- Females.sterr.4
Females.4$Minute <- rep("4", 4)

#Minute 5
Females.5 <- tapply(Females$Context.5min, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.5 <- as.data.frame(Females.5)
Females.5$Exposure <- ActualGroupOrder
colnames(Females.5)[1] <- "Mean" #fix column name
Females.sterr.5 <- tapply(Females$Context.5min, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.5$Sterr <- Females.sterr.5
Females.5$Minute <- rep("5", 4)

#Merge all tables
Females_combined <- rbind(Females.1, Females.2, Females.3, Females.4, Females.5)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
names(Females_combined)[1] <- "Exposure"

#Create error bar data
Females_combined$Upper <- Females_combined$Mean + Females_combined$Sterr
Females_combined$Lower <- Females_combined$Mean - Females_combined$Sterr

Females_combined <- Females_combined %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Graph Female Context Results as a Linegraph
```{r}
png("FC_Females_Context_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

XLabels2 <- c("1", "2", "3", "4", "5")

Females.graph <- ggplot(data=Females_combined, aes(x=Minute, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Females FC Context") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Minute of Experiment")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(Females.graph)
dev.off() 
```
```{r Female FC Context Line Graph, echo = FALSE}
print(Females.graph)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```