---
title: "Fear Conditioning- Reconditioning on Day 8"
author: "Kaylee Helfrich"
date: "6/1/2020-2/24/2021"
output:
  pdf_document: default
  html_document: default
data: "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows fear conditioning data from the rat offspring used for behavior testing. This shows only the analysis of the Reconditioning (Day 8) results. The other results are in separate RMarkdown files. The four treatment groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Fear_Conditioning")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(data.table)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "FearConditioning_ALL_DATA_Freezing_ForAnalysis.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
ActualGroupOrder <- c("MD", "MD+Iron", "PAE", "PAE+Iron")
```
```{r echo = FALSE}
print(data_frame[,c(1:11,32:51)])
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

# Reconditioning Graphs

## Making a data table to graph results from the male reconditioning test
```{r}
#Reconditioning baseline Table
M.Recond.Baseline <- Males %>% select(Exposure, Recond.Baseline)
M.Recond.Baseline$Phase <- strrep("1-Baseline", 1)
names(M.Recond.Baseline)[2] <- "Value"

#Reconditioning tone 1 Table
M.Recond.Tone1 <- Males %>% select(Exposure, Recond.Tone1)
M.Recond.Tone1$Phase <- strrep("2-Tone1", 1)
names(M.Recond.Tone1)[2] <- "Value"

#Reconditioning tone 2 Table
M.Recond.Tone2 <- Males %>% select(Exposure, Recond.Tone2)
M.Recond.Tone2$Phase <- strrep("3-Tone2", 1)
names(M.Recond.Tone2)[2] <- "Value"

#Reconditioning tone 3 Table
M.Recond.Tone3 <- Males %>% select(Exposure, Recond.Tone3)
M.Recond.Tone3$Phase <- strrep("4-Tone3", 1)
names(M.Recond.Tone3)[2] <- "Value"

#Reconditioning tone 4 Table
M.Recond.Tone4 <- Males %>% select(Exposure, Recond.Tone4)
M.Recond.Tone4$Phase <- strrep("5-Tone4", 1)
names(M.Recond.Tone4)[2] <- "Value"

#Reconditioning tone 5 Table
M.Recond.Tone5 <- Males %>% select(Exposure, Recond.Tone5)
M.Recond.Tone5$Phase <- strrep("6-Tone5", 1)
names(M.Recond.Tone5)[2] <- "Value"

#Reconditioning tone 6 Table
M.Recond.Tone6 <- Males %>% select(Exposure, Recond.Tone6)
M.Recond.Tone6$Phase <- strrep("7-Tone6", 1)
names(M.Recond.Tone6)[2] <- "Value"

#Combine Tables
Male.Recond <- rbind(M.Recond.Baseline, M.Recond.Tone1, M.Recond.Tone2, M.Recond.Tone3, M.Recond.Tone4, M.Recond.Tone5, M.Recond.Tone6)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Male.Recond <- Male.Recond %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the male reconditioning results
```{r}
png("FC_Male_Reconditioning_PAExFe_BoxWhisker.png", units = "in", width=12, height=6, res = 300)

Male.Recond.plot <- ggplot(Male.Recond, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Male Fear Conditioning- Reconditioning") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Stage of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("Baseline","Tone 1", "Tone 2", "Tone 3", "Tone 4", "Tone 5", "Tone 6")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Male.Recond.plot)
dev.off()
```
```{r Male Reconditioning Box Whisker, echo = FALSE}
print(Male.Recond.plot)
```

## Making a data table to graph results from the female reconditioning test
```{r}
#Reconditioning baseline Table
F.Recond.Baseline <- Females %>% select(Exposure, Recond.Baseline)
F.Recond.Baseline$Phase <- strrep("1-Baseline", 1)
names(F.Recond.Baseline)[2] <- "Value"

#Reconditioning tone 1 Table
F.Recond.Tone1 <- Females %>% select(Exposure, Recond.Tone1)
F.Recond.Tone1$Phase <- strrep("2-Tone1", 1)
names(F.Recond.Tone1)[2] <- "Value"

#Reconditioning tone 2 Table
F.Recond.Tone2 <- Females %>% select(Exposure, Recond.Tone2)
F.Recond.Tone2$Phase <- strrep("3-Tone2", 1)
names(F.Recond.Tone2)[2] <- "Value"

#Reconditioning tone 3 Table
F.Recond.Tone3 <- Females %>% select(Exposure, Recond.Tone3)
F.Recond.Tone3$Phase <- strrep("4-Tone3", 1)
names(F.Recond.Tone3)[2] <- "Value"

#Reconditioning tone 4 Table
F.Recond.Tone4 <- Females %>% select(Exposure, Recond.Tone4)
F.Recond.Tone4$Phase <- strrep("5-Tone4", 1)
names(F.Recond.Tone4)[2] <- "Value"

#Reconditioning tone 5 Table
F.Recond.Tone5 <- Females %>% select(Exposure, Recond.Tone5)
F.Recond.Tone5$Phase <- strrep("6-Tone5", 1)
names(F.Recond.Tone5)[2] <- "Value"

#Reconditioning tone 6 Table
F.Recond.Tone6 <- Females %>% select(Exposure, Recond.Tone6)
F.Recond.Tone6$Phase <- strrep("7-Tone6", 1)
names(F.Recond.Tone6)[2] <- "Value"

#Combine Tables
Female.Recond <- rbind(F.Recond.Baseline, F.Recond.Tone1, F.Recond.Tone2, F.Recond.Tone3, F.Recond.Tone4, F.Recond.Tone5, F.Recond.Tone6)
neworder <- c("MD", "PAE", "MD+Iron", "PAE+Iron")
Female.Recond <- Female.Recond %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Making a graph of the female reconditioning results
```{r}
png("FC_Female_Reconditioning_PAExFe_BoxWhisker.png", units = "in", width=12, height=6, res = 300)

Female.Recond.plot <- ggplot(Female.Recond, aes(x = Phase, y = Value)) +
  geom_boxplot(aes(fill = Exposure)) +
  ggtitle("Female Fear Conditioning- Reconditioning") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Stage of Test")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+
  scale_x_discrete(labels = c("Baseline","Tone 1", "Tone 2", "Tone 3", "Tone 4", "Tone 5", "Tone 6")) +
  scale_fill_discrete(name = "Exposure Group") +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        #axis.text.x=element_blank(),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.title=element_text(size=20,face="bold"))

print(Female.Recond.plot)
dev.off()
```
```{r Female Reconditioning Box Whisker, echo = FALSE}
print(Female.Recond.plot)
```

# Create line graphs for the reconditioning sessions

## Males
```{r}
#Baseline
Males.1 <- tapply(Males$Recond.Baseline, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.1 <- as.data.frame(Males.1)
Males.1$Exposure <- ActualGroupOrder
colnames(Males.1)[1] <- "Mean" #fix column name
Males.sterr.1 <- tapply(Males$Recond.Baseline, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.1$Sterr <- Males.sterr.1
Males.1$Minute <- rep("1-Baseline", 4)

#Tone1
Males.2 <- tapply(Males$Recond.Tone1, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.2 <- as.data.frame(Males.2)
Males.2$Exposure <- ActualGroupOrder
colnames(Males.2)[1] <- "Mean" #fix column name
Males.sterr.2 <- tapply(Males$Recond.Tone1, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.2$Sterr <- Males.sterr.2
Males.2$Minute <- rep("2-Tone 1", 4)

#Tone2
Males.3 <- tapply(Males$Recond.Tone2, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.3 <- as.data.frame(Males.3)
Males.3$Exposure <- ActualGroupOrder
colnames(Males.3)[1] <- "Mean" #fix column name
Males.sterr.3 <- tapply(Males$Recond.Tone2, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.3$Sterr <- Males.sterr.3
Males.3$Minute <- rep("3-Tone 2", 4)

#Tone3
Males.4 <- tapply(Males$Recond.Tone3, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.4 <- as.data.frame(Males.4)
Males.4$Exposure <- ActualGroupOrder
colnames(Males.4)[1] <- "Mean" #fix column name
Males.sterr.4 <- tapply(Males$Recond.Tone3, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.4$Sterr <- Males.sterr.4
Males.4$Minute <- rep("4-Tone 3", 4)

#Tone4
Males.5 <- tapply(Males$Recond.Tone4, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.5 <- as.data.frame(Males.5)
Males.5$Exposure <- ActualGroupOrder
colnames(Males.5)[1] <- "Mean" #fix column name
Males.sterr.5 <- tapply(Males$Recond.Tone4, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.5$Sterr <- Males.sterr.5
Males.5$Minute <- rep("5-Tone 4", 4)

#Tone5
Males.6 <- tapply(Males$Recond.Tone6, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.6 <- as.data.frame(Males.6)
Males.6$Exposure <- ActualGroupOrder
colnames(Males.6)[1] <- "Mean" #fix column name
Males.sterr.6 <- tapply(Males$Recond.Tone6, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.6$Sterr <- Males.sterr.6
Males.6$Minute <- rep("6-Tone 5", 4)

#Tone6
Males.7 <- tapply(Males$Recond.Tone6, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.7 <- as.data.frame(Males.7)
Males.7$Exposure <- ActualGroupOrder
colnames(Males.7)[1] <- "Mean" #fix column name
Males.sterr.7 <- tapply(Males$Recond.Tone6, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.7$Sterr <- Males.sterr.7
Males.7$Minute <- rep("7-Tone 6", 4)

#Merge all tables
Males_combined <- rbind(Males.1, Males.2, Males.3, Males.4, Males.5, Males.6, Males.7)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
names(Males_combined)[1] <- "Exposure"

#Create error bar data
Males_combined$Upper <- Males_combined$Mean + Males_combined$Sterr
Males_combined$Lower <- Males_combined$Mean - Males_combined$Sterr

Males_combined <- Males_combined %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Graph Male Reconditioning Results as a Linegraph
```{r}
png("FC_Males_Reconditioning_PAExFe_Linegraph.png", units="in", width=12, height=7, res=600) 

XLabels2 <- c(" Baseline", "Tone 1", "Tone 2", "Tone 3", "Tone 4", "Tone 5", "Tone 6")

males.graph <- ggplot(data=Males_combined, aes(x=Minute, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Male FC- Reconditioning") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Phase of Experiment")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(males.graph)
dev.off() 
```
```{r Male FC Reconditioning Line Graph, echo = FALSE}
print(males.graph)
```

## Females
```{r}
#Baseline
Females.1 <- tapply(Females$Recond.Baseline, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.1 <- as.data.frame(Females.1)
Females.1$Exposure <- ActualGroupOrder
colnames(Females.1)[1] <- "Mean" #fix column name
Females.sterr.1 <- tapply(Females$Recond.Baseline, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.1$Sterr <- Females.sterr.1
Females.1$Minute <- rep("1-Baseline", 4)

#Tone1
Females.2 <- tapply(Females$Recond.Tone1, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.2 <- as.data.frame(Females.2)
Females.2$Exposure <- ActualGroupOrder
colnames(Females.2)[1] <- "Mean" #fix column name
Females.sterr.2 <- tapply(Females$Recond.Tone1, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.2$Sterr <- Females.sterr.2
Females.2$Minute <- rep("2-Tone 1", 4)

#Tone2
Females.3 <- tapply(Females$Recond.Tone2, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.3 <- as.data.frame(Females.3)
Females.3$Exposure <- ActualGroupOrder
colnames(Females.3)[1] <- "Mean" #fix column name
Females.sterr.3 <- tapply(Females$Recond.Tone2, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.3$Sterr <- Females.sterr.3
Females.3$Minute <- rep("3-Tone 2", 4)

#Tone3
Females.4 <- tapply(Females$Recond.Tone3, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.4 <- as.data.frame(Females.4)
Females.4$Exposure <- ActualGroupOrder
colnames(Females.4)[1] <- "Mean" #fix column name
Females.sterr.4 <- tapply(Females$Recond.Tone3, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.4$Sterr <- Females.sterr.4
Females.4$Minute <- rep("4-Tone 3", 4)

#Tone4
Females.5 <- tapply(Females$Recond.Tone4, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.5 <- as.data.frame(Females.5)
Females.5$Exposure <- ActualGroupOrder
colnames(Females.5)[1] <- "Mean" #fix column name
Females.sterr.5 <- tapply(Females$Recond.Tone4, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.5$Sterr <- Females.sterr.5
Females.5$Minute <- rep("5-Tone 4", 4)

#Tone5
Females.6 <- tapply(Females$Recond.Tone6, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.6 <- as.data.frame(Females.6)
Females.6$Exposure <- ActualGroupOrder
colnames(Females.6)[1] <- "Mean" #fix column name
Females.sterr.6 <- tapply(Females$Recond.Tone6, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.6$Sterr <- Females.sterr.6
Females.6$Minute <- rep("6-Tone 5", 4)

#Tone6
Females.7 <- tapply(Females$Recond.Tone6, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.7 <- as.data.frame(Females.7)
Females.7$Exposure <- ActualGroupOrder
colnames(Females.7)[1] <- "Mean" #fix column name
Females.sterr.7 <- tapply(Females$Recond.Tone6, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.7$Sterr <- Females.sterr.7
Females.7$Minute <- rep("7-Tone 6", 4)

#Merge all tables
Females_combined <- rbind(Females.1, Females.2, Females.3, Females.4, Females.5, Females.6, Females.7)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
names(Females_combined)[1] <- "Exposure"

#Create error bar data
Females_combined$Upper <- Females_combined$Mean + Females_combined$Sterr
Females_combined$Lower <- Females_combined$Mean - Females_combined$Sterr

Females_combined <- Females_combined %>%
  mutate(Exposure =  factor(Exposure, levels = neworder)) %>%
  arrange(Exposure)
```

## Graph Female Reconditioning Results as a Linegraph
```{r}
png("FC_Females_Reconditioning_PAExFe_Linegraph.png", units="in", width=12, height=7, res=600) 

XLabels2 <- c(" Baseline", "Tone 1", "Tone 2", "Tone 3", "Tone 4", "Tone 5", "Tone 6")

Females.graph <- ggplot(data=Females_combined, aes(x=Minute, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Females FC- Reconditioning") +
  ylab(expression("% Time Freezing")) + 
  xlab(expression("Phase of Experiment")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 14),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
    scale_x_discrete(labels= XLabels2)

print(Females.graph)
dev.off() 
```
```{r Female FC Reconditioning Line Graph, echo = FALSE}
print(Females.graph)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```
