---
title: "Comparing MD and Untreated Offspring Growth P5-P50, and during T-maze Food Deprivation"
author: "Kaylee Helfrich"
date: "2/19/2021-"
output:
  pdf_document: default
  html_document: default
data: "MDvsUntreatedRatGrowth.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/MDvsUntreated")
options(tinytex.verbose = TRUE)
```

# Introduction
These graphs show offspring growth from P5-P50 of only the MD and Untreated rats from the rats generated in the rat iron project in 2020. They also compare growth during the T-maze food deprivation in the MD and untreated groups. This graph includes every rat born from a litter (as long as the litter was dosed correctly), not excluding siblings (except siblings that were sac'd on P22 for the MD group). As long as a rat was weighed, that data is included. None of the data is grouped by litter, and all siblings are included equally. Data are not separated by sex.

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/MDvsUntreated")
library(ggplot2)
library(plotrix)
library(dplyr)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "MDvsUntreatedRatGrowth.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Group), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r}
ActualGroupOrder <- c("2-MD, Females", "1-MD, Males", "4-Untreated, Females", "3-Untreated, Males")
```

# Growth P5-P50

## Create mean and standard deviation tables
```{r}
#Weight at P5
Means.5 <- tapply(data_frame$Weight.P5, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.5 <- as.data.frame(Means.5)
Means.5$Exposure <- ActualGroupOrder
colnames(Means.5)[1] <- "Mean" #fix column name
data_frame.stdev.5 <- tapply(data_frame$Weight.P5, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.5$Stdev <- data_frame.stdev.5
Means.5$Age <- rep("05", 4)

#Weight at P10
Means.10 <- tapply(data_frame$Weight.P10, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.10 <- as.data.frame(Means.10)
Means.10$Exposure <- ActualGroupOrder
colnames(Means.10)[1] <- "Mean" #fix column name
data_frame.stdev.10 <- tapply(data_frame$Weight.P10, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.10$Stdev <- data_frame.stdev.10
Means.10$Age <- rep("10", 4)

#Weight at P15
Means.15 <- tapply(data_frame$Weight.P15, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.15 <- as.data.frame(Means.15)
Means.15$Exposure <- ActualGroupOrder
colnames(Means.15)[1] <- "Mean" #fix column name
data_frame.stdev.15 <- tapply(data_frame$Weight.P15, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.15$Stdev <- data_frame.stdev.15
Means.15$Age <- rep("15", 4)

#Weight at P20
Means.20 <- tapply(data_frame$Weight.P20, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.20 <- as.data.frame(Means.20)
Means.20$Exposure <- ActualGroupOrder
colnames(Means.20)[1] <- "Mean" #fix column name
data_frame.stdev.20 <- tapply(data_frame$Weight.P20, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.20$Stdev <- data_frame.stdev.20
Means.20$Age <- rep("20", 4)

#Weight at P22
Means.22 <- tapply(data_frame$Weight.P22, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.22 <- as.data.frame(Means.22)
Means.22$Exposure <- ActualGroupOrder
colnames(Means.22)[1] <- "Mean" #fix column name
data_frame.stdev.22 <- tapply(data_frame$Weight.P22, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.22$Stdev <- data_frame.stdev.22
Means.22$Age <- rep("22", 4)

#Weight at P28
Means.28 <- tapply(data_frame$Weight.P28, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.28 <- as.data.frame(Means.28)
Means.28$Exposure <- ActualGroupOrder
colnames(Means.28)[1] <- "Mean" #fix column name
data_frame.stdev.28 <- tapply(data_frame$Weight.P28, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.28$Stdev <- data_frame.stdev.28
Means.28$Age <- rep("28", 4)

#Weight at P35
Means.35 <- tapply(data_frame$Weight.P35, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.35 <- as.data.frame(Means.35)
Means.35$Exposure <- ActualGroupOrder
colnames(Means.35)[1] <- "Mean" #fix column name
data_frame.stdev.35 <- tapply(data_frame$Weight.P35, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.35$Stdev <- data_frame.stdev.35
Means.35$Age <- rep("35", 4)

#Weight at P42
Means.42 <- tapply(data_frame$Weight.P42, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.42 <- as.data.frame(Means.42)
Means.42$Exposure <- ActualGroupOrder
colnames(Means.42)[1] <- "Mean" #fix column name
data_frame.stdev.42 <- tapply(data_frame$Weight.P42, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.42$Stdev <- data_frame.stdev.42
Means.42$Age <- rep("42", 4)

#Weight at P50
Means.50 <- tapply(data_frame$Weight.P50, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.50 <- as.data.frame(Means.50)
Means.50$Exposure <- ActualGroupOrder
colnames(Means.50)[1] <- "Mean" #fix column name
data_frame.stdev.50 <- tapply(data_frame$Weight.P50, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.50$Stdev <- data_frame.stdev.50
Means.50$Age <- rep("50", 4)

#Merge all tables
Combined <- rbind(Means.5, Means.10, Means.15, Means.20, Means.22, Means.28, Means.35, Means.42, Means.50)
Combined <- Combined[ ,c(2,1,3,4)]
Combined$Age <- as.numeric(as.vector(Combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
Combined$Upper <- Combined$Mean + Combined$Stdev
Combined$Lower <- Combined$Mean - Combined$Stdev
```

## Graph Growth
```{r}
png("Growth_P5-P50_MDvsUntreated_PAExFe_Linegraph.png", units="in", width=8, height=6, res=600) 

p <- ggplot(data=Combined, aes(x=Age, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,300))+ 
  scale_color_hue(labels = c("MD Males", "MD Females", "Untreated Males", "Untreated Females")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Growth") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Offspring Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
  
print(p)
dev.off() 
```
```{r P5-P50 Weight Gain, echo = FALSE}
print(p)
```

# Growth During T-maze Food deprivation

## Create mean and standard deviation tables
```{r}
#Weight on Saturday
Means.Saturday <- tapply(data_frame$Weight.Sat, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Saturday <- as.data.frame(Means.Saturday)
Means.Saturday$Exposure <- ActualGroupOrder
colnames(Means.Saturday)[1] <- "Mean" #fix column name
data_frame.stdev.Sat <- tapply(data_frame$Weight.Sat, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Saturday$Stdev <- data_frame.stdev.Sat
Means.Saturday$Day <- rep("1-Saturday", 4)

#Weight on Sunday
Means.Sunday <- tapply(data_frame$Weight.Sun, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Sunday <- as.data.frame(Means.Sunday)
Means.Sunday$Exposure <- ActualGroupOrder
colnames(Means.Sunday)[1] <- "Mean" #fix column name
data_frame.stdev.Sun <- tapply(data_frame$Weight.Sun, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Sunday$Stdev <- data_frame.stdev.Sun
Means.Sunday$Day <- rep("2-Sunday", 4)

#Weight on Monday
Means.Monday <- tapply(data_frame$Weight.Mon, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Monday <- as.data.frame(Means.Monday)
Means.Monday$Exposure <- ActualGroupOrder
colnames(Means.Monday)[1] <- "Mean" #fix column name
data_frame.stdev.Mon <- tapply(data_frame$Weight.Mon, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Monday$Stdev <- data_frame.stdev.Mon
Means.Monday$Day <- rep("3-Monday", 4)

#Weight on Tuesday
Means.Tuesday <- tapply(data_frame$Weight.Tues, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Tuesday <- as.data.frame(Means.Tuesday)
Means.Tuesday$Exposure <- ActualGroupOrder
colnames(Means.Tuesday)[1] <- "Mean" #fix column name
data_frame.stdev.Tues <- tapply(data_frame$Weight.Tues, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Tuesday$Stdev <- data_frame.stdev.Tues
Means.Tuesday$Day <- rep("4-Tuesday", 4)

#Weight on Wednesday
Means.Wednesday <- tapply(data_frame$Weight.Wed, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Wednesday <- as.data.frame(Means.Wednesday)
Means.Wednesday$Exposure <- ActualGroupOrder
colnames(Means.Wednesday)[1] <- "Mean" #fix column name
data_frame.stdev.Wed <- tapply(data_frame$Weight.Wed, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Wednesday$Stdev <- data_frame.stdev.Wed
Means.Wednesday$Day <- rep("5-Wednesday", 4)

#Weight on Thursday
Means.Thursday <- tapply(data_frame$Weight.Thurs, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Thursday <- as.data.frame(Means.Thursday)
Means.Thursday$Exposure <- ActualGroupOrder
colnames(Means.Thursday)[1] <- "Mean" #fix column name
data_frame.stdev.Thurs <- tapply(data_frame$Weight.Thurs, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Thursday$Stdev <- data_frame.stdev.Thurs
Means.Thursday$Day <- rep("6-Thursday", 4)

#Weight on Friday
Means.Friday <- tapply(data_frame$Weight.Fri, as.character(data_frame$Group), mean, na.rm=TRUE)
Means.Friday <- as.data.frame(Means.Friday)
Means.Friday$Exposure <- ActualGroupOrder
colnames(Means.Friday)[1] <- "Mean" #fix column name
data_frame.stdev.Fri <- tapply(data_frame$Weight.Fri, as.character(data_frame$Group), sd, na.rm=TRUE)
Means.Friday$Stdev <- data_frame.stdev.Fri
Means.Friday$Day <- rep("7-Friday", 4)

#Merge all tables
Combined <- rbind(Means.Saturday, Means.Sunday, Means.Monday, Means.Tuesday, Means.Wednesday, Means.Thursday, Means.Friday)
Combined <- Combined[ ,c(2,1,3,4)]
Combined$Upper <- Combined$Mean + Combined$Stdev
Combined$Lower <- Combined$Mean - Combined$Stdev
```

## Graph Growth
```{r}
png("WeightDuringTmaze_Sat-Fri_MDvsUntreated_PAExFe_Linegraph.png", units="in", width=12, height=5, res=600) 

XLabels <- c("Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

p <- ggplot(data=Combined, aes(x=Day, y=Mean, group=Exposure, color=Exposure)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200))+ 
  scale_color_hue(labels = c("MD Males", "MD Females", "Untreated Males", "Untreated Females")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Weight Change During T-maze Food Deprivation") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Day of T-maze")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=16, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5),
        axis.title=element_text(size=20,face="bold")) +
  scale_x_discrete(labels= XLabels)
  
print(p)
dev.off() 
```
```{r Weight During Tmaze, echo = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```