---
title: "Offspring Growth P28-P50"
author: "Kaylee Helfrich"
date: "5/29/2020 - 10/30/20"
output:
  pdf_document: default
  html_document: default
data: "Adolescent_Offspring_LateGrowth_Postnatal.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Offspring_Growth_Late")
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows offspring growth from P28-P50 of the offspring selected for behavioral testing from the rats generated in the rat iron project in 2020. This graph includes only 0-3 males and 0-3 females per litter from the litters selected for behavioral testing. Note that not all of the siblings from each litter are included. Rats selected for behavior were selected on the basis of the median litter weight on P15. None of the data is grouped by litter. The four Exposure groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female.

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Offspring_Growth_Late")
library(ggplot2)
library(plotrix)
library(dplyr)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by Exposure to be alphabetical}
File <- "Adolescent_Offspring_LateGrowth_Postnatal.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r}
ActualGroupOrder <- c("MD", "MD+iron", "PAE", "PAE+iron")
#GraphGroupOrder <- c("MD+water", "PAE+water", "MD+iron", "PAE+iron")
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

## Create mean and standard deviation tables for males
```{r}
#Weight at P28
Males.means.28 <- tapply(Males$Weight.P28, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.28 <- as.data.frame(Males.means.28)
Males.means.28$Exposure <- ActualGroupOrder
colnames(Males.means.28)[1] <- "Mean" #fix column name
Males.stdev.28 <- tapply(Males$Weight.P28, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.28$Stdev <- Males.stdev.28
Males.means.28$Age <- rep("28", 4)

#Weight at P35
Males.means.35 <- tapply(Males$Weight.P35, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.35 <- as.data.frame(Males.means.35)
Males.means.35$Exposure <- ActualGroupOrder
colnames(Males.means.35)[1] <- "Mean" #fix column name
Males.stdev.35 <- tapply(Males$Weight.P35, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.35$Stdev <- Males.stdev.35
Males.means.35$Age <- rep("35", 4)

#Weight at P42
Males.means.42 <- tapply(Males$Weight.P42, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.42 <- as.data.frame(Males.means.42)
Males.means.42$Exposure <- ActualGroupOrder
colnames(Males.means.42)[1] <- "Mean" #fix column name
Males.stdev.42 <- tapply(Males$Weight.P42, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.42$Stdev <- Males.stdev.42
Males.means.42$Age <- rep("42", 4)

#Weight at P50
Males.means.50 <- tapply(Males$Weight.P50, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.50 <- as.data.frame(Males.means.50)
Males.means.50$Exposure <- ActualGroupOrder
colnames(Males.means.50)[1] <- "Mean" #fix column name
Males.stdev.50 <- tapply(Males$Weight.P50, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.50$Stdev <- Males.stdev.50
Males.means.50$Age <- rep("50", 4)

#Merge all tables
Males_combined <- rbind(Males.means.28, Males.means.35, Males.means.42, Males.means.50)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
Males_combined$Age <- as.numeric(as.vector(Males_combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(Males_combined)[1] <- "Exposure.Group"
Males_combined$Upper <- Males_combined$Mean + Males_combined$Stdev
Males_combined$Lower <- Males_combined$Mean - Males_combined$Stdev

Males_combined$Exposure.Group <- factor(Males_combined$Exposure.Group, levels=c("MD", "PAE", "MD+iron", "PAE+iron"))
```

## Graph Male Weights
```{r}
png("MaleWeight_P28-P50_AllData_PAExFe_Linegraph_B&W.png", units="in", width=8, height=6, res=600) 

males <- ggplot(data=Males_combined, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,225))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                             "PAE" = "#000000",
                             "MD+iron" = "#000000",
                             "PAE+iron" = "#000000"
                             )) +
  ggtitle("Males, P28 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20, face="bold", family = "Times New Roman"),
        legend.title=element_text(family = "Times New Roman"), 
        legend.text=element_text(family = "Times New Roman"))
  
print(males)
dev.off() 
```
```{r Male P28-P50 Weight, echo = FALSE}
print(males)
```

## Create mean and standard deviation tables for females
```{r}
#Weight at P28
Females.means.28 <- tapply(Females$Weight.P28, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.28 <- as.data.frame(Females.means.28)
Females.means.28$Exposure <- ActualGroupOrder
colnames(Females.means.28)[1] <- "Mean" #fix column name
Females.stdev.28 <- tapply(Females$Weight.P28, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.28$Stdev <- Females.stdev.28
Females.means.28$Age <- rep("28", 4)

#Weight at P35
Females.means.35 <- tapply(Females$Weight.P35, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.35 <- as.data.frame(Females.means.35)
Females.means.35$Exposure <- ActualGroupOrder
colnames(Females.means.35)[1] <- "Mean" #fix column name
Females.stdev.35 <- tapply(Females$Weight.P35, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.35$Stdev <- Females.stdev.35
Females.means.35$Age <- rep("35", 4)

#Weight at P42
Females.means.42 <- tapply(Females$Weight.P42, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.42 <- as.data.frame(Females.means.42)
Females.means.42$Exposure <- ActualGroupOrder
colnames(Females.means.42)[1] <- "Mean" #fix column name
Females.stdev.42 <- tapply(Females$Weight.P42, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.42$Stdev <- Females.stdev.42
Females.means.42$Age <- rep("42", 4)

#Weight at P50
Females.means.50 <- tapply(Females$Weight.P50, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.50 <- as.data.frame(Females.means.50)
Females.means.50$Exposure <- ActualGroupOrder
colnames(Females.means.50)[1] <- "Mean" #fix column name
Females.stdev.50 <- tapply(Females$Weight.P50, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.50$Stdev <- Females.stdev.50
Females.means.50$Age <- rep("50", 4)

#Merge all tables
Females_combined <- rbind(Females.means.28, Females.means.35, Females.means.42, Females.means.50)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
Females_combined$Age <- as.numeric(as.vector(Females_combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(Females_combined)[1] <- "Exposure.Group"
Females_combined$Upper <- Females_combined$Mean + Females_combined$Stdev
Females_combined$Lower <- Females_combined$Mean - Females_combined$Stdev

Females_combined$Exposure.Group <- factor(Females_combined$Exposure.Group, levels=c("MD", "PAE", "MD+iron", "PAE+iron"))
```

## Graph Female Weights
```{r}
png("FemaleWeight_P28-P50_AllData_PAExFe_Linegraph_B&W.png", units="in", width=8, height=6, res=600) 

females <- ggplot(data=Females_combined, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,225))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                             "PAE" = "#000000",
                             "MD+iron" = "#000000",
                             "PAE+iron" = "#000000"
                             )) +
  ggtitle("Females, P28 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20, face="bold", family = "Times New Roman"),
        legend.title=element_text(family = "Times New Roman"), 
        legend.text=element_text(family = "Times New Roman"))
  
print(females)
dev.off() 
```
```{r Female P28-P50 Weight, echo = FALSE}
print(females)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```