---
title: "Offspring Growth P5-P50, Only Including Those For Behavior"
author: "Kaylee Helfrich"
date: "5/22/2020 - 5/7/2021"
output:
  pdf_document: default
  html_document: default
data: "Offspring_Growth_P5-P50_AllBehaviorRats_Females_ForGraphing.csv"
      "Offspring_Growth_P5-P50_AllBehaviorRats_Males_ForGraphing.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Offspring_Growth_AllBehaviorRats")
options(tinytex.verbose = TRUE)
```

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Offspring_Growth_AllBehaviorRats")
library(ggplot2)
library(plotrix)
library(dplyr)
library(extrafont)
loadfonts(device = "win")
```

# Males
```{r Import file and rearrange by Exposure to be alphabetical}
File <- "Offspring_Growth_P5-P50_AllBehaviorRats_Males_ForGraphing.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r}
ActualGroupOrder <- c("MD", "MD+iron", "PAE", "PAE+iron")
#GraphGroupOrder <- c("MD+water", "PAE+water", "MD+iron", "PAE+iron")
```

## Create mean and standard deviation tables for males
```{r}
#Weight at P5
Males.means.5 <- tapply(data_frame$Weight.P5, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.5 <- as.data.frame(Males.means.5)
Males.means.5$Exposure <- ActualGroupOrder
colnames(Males.means.5)[1] <- "Mean" #fix column name
Males.stdev.5 <- tapply(data_frame$Weight.P5, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.5$Stdev <- Males.stdev.5
Males.means.5$Age <- rep("05", 4)

#Weight at P10
Males.means.10 <- tapply(data_frame$Weight.P10, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.10 <- as.data.frame(Males.means.10)
Males.means.10$Exposure <- ActualGroupOrder
colnames(Males.means.10)[1] <- "Mean" #fix column name
Males.stdev.10 <- tapply(data_frame$Weight.P10, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.10$Stdev <- Males.stdev.10
Males.means.10$Age <- rep("10", 4)

#Weight at P15
Males.means.15 <- tapply(data_frame$Weight.P15, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.15 <- as.data.frame(Males.means.15)
Males.means.15$Exposure <- ActualGroupOrder
colnames(Males.means.15)[1] <- "Mean" #fix column name
Males.stdev.15 <- tapply(data_frame$Weight.P15, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.15$Stdev <- Males.stdev.15
Males.means.15$Age <- rep("15", 4)

#Weight at P20
Males.means.20 <- tapply(data_frame$Weight.P20, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.20 <- as.data.frame(Males.means.20)
Males.means.20$Exposure <- ActualGroupOrder
colnames(Males.means.20)[1] <- "Mean" #fix column name
Males.stdev.20 <- tapply(data_frame$Weight.P20, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.20$Stdev <- Males.stdev.20
Males.means.20$Age <- rep("20", 4)

#Weight at P22
Males.means.22 <- tapply(data_frame$Weight.P22, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.22 <- as.data.frame(Males.means.22)
Males.means.22$Exposure <- ActualGroupOrder
colnames(Males.means.22)[1] <- "Mean" #fix column name
Males.stdev.22 <- tapply(data_frame$Weight.P22, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.22$Stdev <- Males.stdev.22
Males.means.22$Age <- rep("22", 4)

#Weight at P28
Males.means.28 <- tapply(data_frame$Weight.P28, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.28 <- as.data.frame(Males.means.28)
Males.means.28$Exposure <- ActualGroupOrder
colnames(Males.means.28)[1] <- "Mean" #fix column name
Males.stdev.28 <- tapply(data_frame$Weight.P28, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.28$Stdev <- Males.stdev.28
Males.means.28$Age <- rep("28", 4)

#Weight at P35
Males.means.35 <- tapply(data_frame$Weight.P35, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.35 <- as.data.frame(Males.means.35)
Males.means.35$Exposure <- ActualGroupOrder
colnames(Males.means.35)[1] <- "Mean" #fix column name
Males.stdev.35 <- tapply(data_frame$Weight.P35, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.35$Stdev <- Males.stdev.35
Males.means.35$Age <- rep("35", 4)

#Weight at P42
Males.means.42 <- tapply(data_frame$Weight.P42, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.42 <- as.data.frame(Males.means.42)
Males.means.42$Exposure <- ActualGroupOrder
colnames(Males.means.42)[1] <- "Mean" #fix column name
Males.stdev.42 <- tapply(data_frame$Weight.P42, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.42$Stdev <- Males.stdev.42
Males.means.42$Age <- rep("42", 4)

#Weight at P50
Males.means.50 <- tapply(data_frame$Weight.P50, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Males.means.50 <- as.data.frame(Males.means.50)
Males.means.50$Exposure <- ActualGroupOrder
colnames(Males.means.50)[1] <- "Mean" #fix column name
Males.stdev.50 <- tapply(data_frame$Weight.P50, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Males.means.50$Stdev <- Males.stdev.50
Males.means.50$Age <- rep("50", 4)

#Merge all tables
Males_combined <- rbind(Males.means.5, Males.means.10, Males.means.15, Males.means.20, Males.means.22, Males.means.28, Males.means.35, Males.means.42, Males.means.50)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
Males_combined$Age <- as.numeric(as.vector(Males_combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(Males_combined)[1] <- "Exposure.Group"
Males_combined$Upper <- Males_combined$Mean + Males_combined$Stdev
Males_combined$Lower <- Males_combined$Mean - Males_combined$Stdev

Males_combined$Exposure.Group <- factor(Males_combined$Exposure.Group, levels=c("MD", "PAE", "MD+iron", "PAE+iron"))
```

## Individual dataframes for visualizing each line
```{r}
MC_MD <- Males_combined[ which(Males_combined$Exposure.Group=='MD'), ]
MC_PAE <- Males_combined[ which(Males_combined$Exposure.Group=='PAE'), ]
MC_MDFe <- Males_combined[ which(Males_combined$Exposure.Group=='MD+iron'), ]
MC_PAEFe <- Males_combined[ which(Males_combined$Exposure.Group=='PAE+iron'), ]

MC_MDPAE<- rbind(MC_MD, MC_PAE)
MC_MDPAEMDiron <- rbind(MC_MD, MC_PAE, MC_MDFe)
MC_MDPAEMDironPAEiron <- rbind(MC_MD, MC_PAE, MC_MDFe, MC_PAEFe)
```

## Graph Male Weights- MD only
```{r}
png("MaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_MDonly.png", units="in", width=8, height=6, res=600) 

males <- ggplot(data=MC_MD, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  #scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  #scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#CC0000")) +
                            # "PAE" = "#FFFFFF",
                            # "MD+iron" = "#FFFFFF",
                            # "PAE+iron" = "#FFFFFF"
                            # )) +
  ggtitle("Males, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(males)
dev.off() 
```
```{r Male P5-P50 Weight, echo = FALSE}
print(males)
```

## Graph Male Weights- MD and PAE only
```{r}
png("MaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_MDPAE.png", units="in", width=8, height=6, res=600) 

males <- ggplot(data=MC_MDPAE, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  scale_color_hue(labels = c("MD", "PAE")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                              "PAE" = "#CC0000"
                            # "MD+iron" = "#FFFFFF",
                            # "PAE+iron" = "#FFFFFF"
                             )) +
  ggtitle("Males, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(males)
dev.off() 
```
```{r Male P5-P50 Weight, echo = FALSE}
print(males)
```

## Graph Male Weights- MD, PAE, MD + iron only
```{r}
png("MaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_MDPAEMDFe.png", units="in", width=8, height=6, res=600) 

males <- ggplot(data=MC_MDPAEMDiron, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dashed")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                              "PAE" = "#000000",
                              "MD+iron" = "#CC0000"
                            # "PAE+iron" = "#FFFFFF"
                             )) +
  ggtitle("Males, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(males)
dev.off() 
```
```{r Male P5-P50 Weight, echo = FALSE}
print(males)
```

## Graph Male Weights- All
```{r}
png("MaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_All.png", units="in", width=8, height=6, res=600) 

males <- ggplot(data=MC_MDPAEMDironPAEiron, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dashed", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                              "PAE" = "#000000",
                              "MD+iron" = "#000000",
                             "PAE+iron" = "#CC0000"
                             )) +
  ggtitle("Males, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(males)
dev.off() 
```
```{r Male P5-P50 Weight, echo = FALSE}
print(males)
```

# Females
```{r Import file and rearrange by Exposure to be alphabetical}
File <- "Offspring_Growth_P5-P50_AllBehaviorRats_Females_ForGraphing.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r}
ActualGroupOrder <- c("MD", "MD+iron", "PAE", "PAE+iron")
#GraphGroupOrder <- c("MD+water", "PAE+water", "MD+iron", "PAE+iron")
```

## Create mean and standard deviation tables for females
```{r}
#Weight at P5
Females.means.5 <- tapply(data_frame$Weight.P5, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.5 <- as.data.frame(Females.means.5)
Females.means.5$Exposure <- ActualGroupOrder
colnames(Females.means.5)[1] <- "Mean" #fix column name
Females.stdev.5 <- tapply(data_frame$Weight.P5, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.5$Stdev <- Females.stdev.5
Females.means.5$Age <- rep("05", 4)

#Weight at P10
Females.means.10 <- tapply(data_frame$Weight.P10, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.10 <- as.data.frame(Females.means.10)
Females.means.10$Exposure <- ActualGroupOrder
colnames(Females.means.10)[1] <- "Mean" #fix column name
Females.stdev.10 <- tapply(data_frame$Weight.P10, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.10$Stdev <- Females.stdev.10
Females.means.10$Age <- rep("10", 4)

#Weight at P15
Females.means.15 <- tapply(data_frame$Weight.P15, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.15 <- as.data.frame(Females.means.15)
Females.means.15$Exposure <- ActualGroupOrder
colnames(Females.means.15)[1] <- "Mean" #fix column name
Females.stdev.15 <- tapply(data_frame$Weight.P15, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.15$Stdev <- Females.stdev.15
Females.means.15$Age <- rep("15", 4)

#Weight at P20
Females.means.20 <- tapply(data_frame$Weight.P20, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.20 <- as.data.frame(Females.means.20)
Females.means.20$Exposure <- ActualGroupOrder
colnames(Females.means.20)[1] <- "Mean" #fix column name
Females.stdev.20 <- tapply(data_frame$Weight.P20, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.20$Stdev <- Females.stdev.20
Females.means.20$Age <- rep("20", 4)

#Weight at P22
Females.means.22 <- tapply(data_frame$Weight.P22, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.22 <- as.data.frame(Females.means.22)
Females.means.22$Exposure <- ActualGroupOrder
colnames(Females.means.22)[1] <- "Mean" #fix column name
Females.stdev.22 <- tapply(data_frame$Weight.P22, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.22$Stdev <- Females.stdev.22
Females.means.22$Age <- rep("22", 4)

#Weight at P28
Females.means.28 <- tapply(data_frame$Weight.P28, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.28 <- as.data.frame(Females.means.28)
Females.means.28$Exposure <- ActualGroupOrder
colnames(Females.means.28)[1] <- "Mean" #fix column name
Females.stdev.28 <- tapply(data_frame$Weight.P28, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.28$Stdev <- Females.stdev.28
Females.means.28$Age <- rep("28", 4)

#Weight at P35
Females.means.35 <- tapply(data_frame$Weight.P35, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.35 <- as.data.frame(Females.means.35)
Females.means.35$Exposure <- ActualGroupOrder
colnames(Females.means.35)[1] <- "Mean" #fix column name
Females.stdev.35 <- tapply(data_frame$Weight.P35, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.35$Stdev <- Females.stdev.35
Females.means.35$Age <- rep("35", 4)

#Weight at P42
Females.means.42 <- tapply(data_frame$Weight.P42, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.42 <- as.data.frame(Females.means.42)
Females.means.42$Exposure <- ActualGroupOrder
colnames(Females.means.42)[1] <- "Mean" #fix column name
Females.stdev.42 <- tapply(data_frame$Weight.P42, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.42$Stdev <- Females.stdev.42
Females.means.42$Age <- rep("42", 4)

#Weight at P50
Females.means.50 <- tapply(data_frame$Weight.P50, as.character(data_frame$Exposure), mean, na.rm=TRUE)
Females.means.50 <- as.data.frame(Females.means.50)
Females.means.50$Exposure <- ActualGroupOrder
colnames(Females.means.50)[1] <- "Mean" #fix column name
Females.stdev.50 <- tapply(data_frame$Weight.P50, as.character(data_frame$Exposure), sd, na.rm=TRUE)
Females.means.50$Stdev <- Females.stdev.50
Females.means.50$Age <- rep("50", 4)

#Merge all tables
Females_combined <- rbind(Females.means.5, Females.means.10, Females.means.15, Females.means.20, Females.means.22, Females.means.28, Females.means.35, Females.means.42, Females.means.50)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
Females_combined$Age <- as.numeric(as.vector(Females_combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(Females_combined)[1] <- "Exposure.Group"
Females_combined$Upper <- Females_combined$Mean + Females_combined$Stdev
Females_combined$Lower <- Females_combined$Mean - Females_combined$Stdev

Females_combined$Exposure.Group <- factor(Females_combined$Exposure.Group, levels=c("MD", "PAE", "MD+iron", "PAE+iron"))
```

## Individual dataframes for visualizing each line
```{r}
FC_MD <- Females_combined[ which(Females_combined$Exposure.Group=='MD'), ]
FC_PAE <- Females_combined[ which(Females_combined$Exposure.Group=='PAE'), ]
FC_MDFe <- Females_combined[ which(Females_combined$Exposure.Group=='MD+iron'), ]
FC_PAEFe <- Females_combined[ which(Females_combined$Exposure.Group=='PAE+iron'), ]

FC_MDPAE<- rbind(FC_MD, FC_PAE)
FC_MDPAEMDiron <- rbind(FC_MD, FC_PAE, FC_MDFe)
FC_MDPAEMDironPAEiron <- rbind(FC_MD, FC_PAE, FC_MDFe, FC_PAEFe)
```

## Graph Female Weights- MD only
```{r}
png("FemaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_MDonly.png", units="in", width=8, height=6, res=600) 

Females <- ggplot(data=FC_MD, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  #scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  #scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#CC0000")) +
                            # "PAE" = "#FFFFFF",
                            # "MD+iron" = "#FFFFFF",
                            # "PAE+iron" = "#FFFFFF"
                            # )) +
  ggtitle("Females, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(Females)
dev.off() 
```
```{r Female P5-P50 Weight, echo = FALSE}
print(Females)
```

## Graph Female Weights- MD and PAE only
```{r}
png("FemaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_MDPAE.png", units="in", width=8, height=6, res=600) 

Females <- ggplot(data=FC_MDPAE, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  scale_color_hue(labels = c("MD", "PAE")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                              "PAE" = "#CC0000"
                            # "MD+iron" = "#FFFFFF",
                            # "PAE+iron" = "#FFFFFF"
                             )) +
  ggtitle("Females, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(Females)
dev.off() 
```
```{r Female P5-P50 Weight, echo = FALSE}
print(Females)
```

## Graph Female Weights- MD, PAE, MD + iron only
```{r}
png("FemaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_MDPAEMDFe.png", units="in", width=8, height=6, res=600) 

Females <- ggplot(data=FC_MDPAEMDiron, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dashed")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                              "PAE" = "#000000",
                              "MD+iron" = "#CC0000"
                            # "PAE+iron" = "#FFFFFF"
                             )) +
  ggtitle("Females, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(Females)
dev.off() 
```
```{r Female P5-P50 Weight, echo = FALSE}
print(Females)
```

## Graph Female Weights- All
```{r}
png("FemaleWeight_P5-P50_RatsForBehavior_PAExFe_Linegraph_ForASN_All.png", units="in", width=8, height=6, res=600) 

Females <- ggplot(data=FC_MDPAEMDironPAEiron, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dashed", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                              "PAE" = "#000000",
                              "MD+iron" = "#000000",
                             "PAE+iron" = "#CC0000"
                             )) +
  ggtitle("Females, P5 - P50") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Arial"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Arial"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Arial"),
        axis.title=element_text(size=20, face="bold", family = "Arial"),
        legend.title=element_text(family = "Arial"), 
        legend.text=element_text(family = "Arial"))
  
print(Females)
dev.off() 
```
```{r Female P5-P50 Weight, echo = FALSE}
print(Females)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```