---
title: "Offspring Growth P5-P22, Only Including Those For Behavior"
author: "Kaylee Helfrich"
date: "5/22/2020 - 10/30/2020"
output:
  pdf_document: default
  html_document: default
data: "Offspring_Growth_EarlyPostnatal.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Offspring_Growth_Early")
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows offspring growth from P5-P22 for only the offspring that were later used for behavior (the 3 males and 3 females that had the median weight of the litter) from the rats generated in the rat iron project in 2020. None of the data is grouped by litter, and all siblings are included equally. The four Exposure groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female.

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Offspring_Growth_Early")
library(ggplot2)
library(plotrix)
library(dplyr)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by Exposure to be alphabetical}
File <- "Offspring_Growth_EarlyPostnatal.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
data_frame <- data_frame[ which(data_frame$Behavior=='Yes'), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r}
ActualGroupOrder <- c("CON", "CON+Iron", "ALC", "ALC+Iron")
#GraphGroupOrder <- c("MD+water", "PAE+water", "MD+iron", "PAE+iron")
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

## Create mean and standard deviation tables for males
```{r}
#Weight at P5
Males.means.5 <- tapply(Males$Weight.P5, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.5 <- as.data.frame(Males.means.5)
Males.means.5$Exposure <- ActualGroupOrder
colnames(Males.means.5)[1] <- "Mean" #fix column name
Males.stdev.5 <- tapply(Males$Weight.P5, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.5$Stdev <- Males.stdev.5
Males.means.5$Age <- rep("05", 4)

#Weight at P10
Males.means.10 <- tapply(Males$Weight.P10, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.10 <- as.data.frame(Males.means.10)
Males.means.10$Exposure <- ActualGroupOrder
colnames(Males.means.10)[1] <- "Mean" #fix column name
Males.stdev.10 <- tapply(Males$Weight.P10, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.10$Stdev <- Males.stdev.10
Males.means.10$Age <- rep("10", 4)

#Weight at P15
Males.means.15 <- tapply(Males$Weight.P15, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.15 <- as.data.frame(Males.means.15)
Males.means.15$Exposure <- ActualGroupOrder
colnames(Males.means.15)[1] <- "Mean" #fix column name
Males.stdev.15 <- tapply(Males$Weight.P15, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.15$Stdev <- Males.stdev.15
Males.means.15$Age <- rep("15", 4)

#Weight at P20
Males.means.20 <- tapply(Males$Weight.P20, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.20 <- as.data.frame(Males.means.20)
Males.means.20$Exposure <- ActualGroupOrder
colnames(Males.means.20)[1] <- "Mean" #fix column name
Males.stdev.20 <- tapply(Males$Weight.P20, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.20$Stdev <- Males.stdev.20
Males.means.20$Age <- rep("20", 4)

#Weight at P22
Males.means.22 <- tapply(Males$Weight.P22, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.means.22 <- as.data.frame(Males.means.22)
Males.means.22$Exposure <- ActualGroupOrder
colnames(Males.means.22)[1] <- "Mean" #fix column name
Males.stdev.22 <- tapply(Males$Weight.P22, as.character(Males$Exposure), sd, na.rm=TRUE)
Males.means.22$Stdev <- Males.stdev.22
Males.means.22$Age <- rep("22", 4)

#Merge all tables
Males_combined <- rbind(Males.means.5, Males.means.10, Males.means.15, Males.means.20, Males.means.22)
Males_combined <- Males_combined[ ,c(2,1,3,4)]
Males_combined$Age <- as.numeric(as.vector(Males_combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(Males_combined)[1] <- "Exposure.Group"
Males_combined$Upper <- Males_combined$Mean + Males_combined$Stdev
Males_combined$Lower <- Males_combined$Mean - Males_combined$Stdev

Males_combined$Exposure.Group <- factor(Males_combined$Exposure.Group, levels=c("CON", "ALC", "CON+Iron", "ALC+Iron"))
```

## Graph Male Weights
```{r}
png("MaleWeight_P5-P22_RatsForBehavior_PAExFe_Linegraph_B&W.png", units="in", width=8, height=6, res=600) 

males <- ggplot(data=Males_combined, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,50))+ 
  scale_color_hue(labels = c("CON", "ALC", "CON+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("CON" = "#000000",
                             "ALC" = "#000000",
                             "CON+Iron" = "#000000",
                             "ALC+Iron" = "#000000"
                             )) +
  ggtitle("Males, P5 - P22") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20, face="bold", family = "Times New Roman"),
        legend.title=element_text(family = "Times New Roman"), 
        legend.text=element_text(family = "Times New Roman"))
  
print(males)
dev.off() 
```
```{r Male P5-P22 Weight, echo = FALSE}
print(males)
```

## Create mean and standard deviation tables for females
```{r}
#Weight at P5
Females.means.5 <- tapply(Females$Weight.P5, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.5 <- as.data.frame(Females.means.5)
Females.means.5$Exposure <- ActualGroupOrder
colnames(Females.means.5)[1] <- "Mean" #fix column name
Females.stdev.5 <- tapply(Females$Weight.P5, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.5$Stdev <- Females.stdev.5
Females.means.5$Age <- rep("05", 4)

#Weight at P10
Females.means.10 <- tapply(Females$Weight.P10, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.10 <- as.data.frame(Females.means.10)
Females.means.10$Exposure <- ActualGroupOrder
colnames(Females.means.10)[1] <- "Mean" #fix column name
Females.stdev.10 <- tapply(Females$Weight.P10, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.10$Stdev <- Females.stdev.10
Females.means.10$Age <- rep("10", 4)

#Weight at P15
Females.means.15 <- tapply(Females$Weight.P15, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.15 <- as.data.frame(Females.means.15)
Females.means.15$Exposure <- ActualGroupOrder
colnames(Females.means.15)[1] <- "Mean" #fix column name
Females.stdev.15 <- tapply(Females$Weight.P15, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.15$Stdev <- Females.stdev.15
Females.means.15$Age <- rep("15", 4)

#Weight at P20
Females.means.20 <- tapply(Females$Weight.P20, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.20 <- as.data.frame(Females.means.20)
Females.means.20$Exposure <- ActualGroupOrder
colnames(Females.means.20)[1] <- "Mean" #fix column name
Females.stdev.20 <- tapply(Females$Weight.P20, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.20$Stdev <- Females.stdev.20
Females.means.20$Age <- rep("20", 4)

#Weight at P22
Females.means.22 <- tapply(Females$Weight.P22, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.means.22 <- as.data.frame(Females.means.22)
Females.means.22$Exposure <- ActualGroupOrder
colnames(Females.means.22)[1] <- "Mean" #fix column name
Females.stdev.22 <- tapply(Females$Weight.P22, as.character(Females$Exposure), sd, na.rm=TRUE)
Females.means.22$Stdev <- Females.stdev.22
Females.means.22$Age <- rep("22", 4)

#Merge all tables
Females_combined <- rbind(Females.means.5, Females.means.10, Females.means.15, Females.means.20, Females.means.22)
Females_combined <- Females_combined[ ,c(2,1,3,4)]
Females_combined$Age <- as.numeric(as.vector(Females_combined$Age)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(Females_combined)[1] <- "Exposure.Group"
Females_combined$Upper <- Females_combined$Mean + Females_combined$Stdev
Females_combined$Lower <- Females_combined$Mean - Females_combined$Stdev

Females_combined$Exposure.Group <- factor(Females_combined$Exposure.Group, levels=c("MD", "PAE", "MD+iron", "PAE+iron"))
```

## Graph Female Weights
```{r}
png("FemaleWeight_P5-P22_RatsForBehavior_PAExFe_Linegraph_B&W.png", units="in", width=8, height=6, res=600) 

females <- ggplot(data=Females_combined, aes(x=Age, y=Mean, group=Exposure.Group)) +
  geom_point(aes(shape=Exposure.Group)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure.Group, color = Exposure.Group)) +
  scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,50))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  scale_color_manual(values=c("MD" = "#000000",
                             "PAE" = "#000000",
                             "MD+iron" = "#000000",
                             "PAE+iron" = "#000000"
                             )) +
  ggtitle("Females, P5 - P22") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Age (days post-birth)")) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 16, ),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.5, family = "Times New Roman"),
        axis.title=element_text(size=20, face="bold", family = "Times New Roman"),
        legend.title=element_text(family = "Times New Roman"), 
        legend.text=element_text(family = "Times New Roman"))
  
print(females)
dev.off() 
```
```{r Female P5-P22 Weight, echo = FALSE}
print(females)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```