---
title: "Offspring Performance on the Open Field test, AIN-76A diet with MD or Alcohol and Iron Supplement or Water- P28"
author: "Kaylee Helfrich"
date: "1/25/2021-"
output: 
  pdf_document: default
  html_document: default
data: "OpenFieldData_CLEAN.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Open_Field")
options(tinytex.verbose = TRUE)
```

# Graphing Data from the Open Field Test
This document details my graphing of the data from offspring activity and lcoation in the open field test. This analysis uses all data that was collected. No other samples were excluded because there was no good rationale for the exclusion of any other samples. Data were collected from batches 1-5 on postnatal day 28. Rachel Hodges and Kaylee Helfrich were responsible for running the rats on the open field. Rats' mothers were Long-Evans rats that were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5 and also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. The offspring were weaned on P22, and then handled daily for approximately 2-3 minutes per day until they were run on the EPM and the open field. See experimental notes for more information on how the open field was laid out and how data was analyzed on Ethovision. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups, as well as males vs. females. Statistical analysis in JMP will use 3-way ANOVA to assign significance to the measures (male vs female, alcohol vs. MD, iron vs. water). 

# Importing Files and Arranging Data
```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/Open_Field")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "OpenFieldData_CLEAN.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("CON", "CON+Iron","PAE", "PAE+Iron")
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Rat.Sex=='M'), ]
Females <- data_frame[ which(data_frame$Rat.Sex=='F'), ]
```

## Males- Equalize Row Number by Exposure
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Males %>% count(Exposure) #Calculate how many individual Males there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Exposure <- ActualGroupOrder #add new column so that # of points to be added is assigned to exposure
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
MDH2O <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
MDFe <- DiffPoints[2,1]
AlcH2O <- DiffPoints[3,1]
AlcFe <- DiffPoints[4,1] 

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 20)) #create an empty dataframe filled with NA's
vector <- rep(c("CON", "CON+Iron", "PAE", "PAE+Iron"), times = c(MDH2O, MDFe, AlcH2O, AlcFe)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Exposure <- vector #add in the Exposure column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1:3,21,4:20)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Males)) #set the names of the new df to match the original df
Males_new <- rbind(Males, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Males_new %>% count(Exposure)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Males_new <- Males_new[order(Males_new$Exposure), ]
Male_NumPoints <- NumPoints
```
### Number of Missing Points to Expect in Male Graphs
```{r echo = FALSE}
print(Nrow)
```

## Females- Equalize Row Number by Exposure
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Females %>% count(Exposure) #Calculate how many individual Females there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Exposure <- ActualGroupOrder #add new column so that # of points to be added is assigned to exposure
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
MDH2O <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
MDFe <- DiffPoints[2,1]
AlcH2O <- DiffPoints[3,1]
AlcFe <- DiffPoints[4,1] 

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 20)) #create an empty dataframe filled with NA's
vector <- rep(c("CON", "CON+Iron", "PAE", "PAE+Iron"), times = c(MDH2O, MDFe, AlcH2O, AlcFe)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Exposure <- vector #add in the Exposure column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1:3,21,4:20)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Females)) #set the names of the new df to match the original df
Females_new <- rbind(Females, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Females_new %>% count(Exposure)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Females_new <- Females_new[order(Females_new$Exposure), ]
Female_NumPoints <- NumPoints
```
### Number of Missing Points to Expect in Female Graphs
```{r echo = FALSE}
print(Nrow)
```

# Total Distance Moved

## Males- Distance Moved
This code is virtually the same for all bar graphs with overlaid points, so future graphs do not have the full code included in the RMarkdown file.
```{r, warning = FALSE, message = FALSE}
#Mean- calculate mean for column, repeat it to number of points, and create dataframe
Mean <- tapply(Males_new$TotalDistance.CP.cm, as.character(Males_new$Exposure), mean, na.rm=TRUE) #make sure to change selected column to change data for graph
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints)) #repeat mean a set number of times
Mean$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints) #repeat treatment a set number of times
colnames(Mean)[1] <- "Mean" #fix column name

#Stdev- calculate standard deviation for column, repeat it to number of points, and create dataframe
Stdev <- tapply(Males_new$TotalDistance.CP.cm, as.character(Males_new$Exposure), sd, na.rm=TRUE) #make sure to change selected column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints)) #repeat stdev a set number of times
Stdev$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints) #repeat treatment a set number of times
colnames(Stdev)[1] <- "Stdev" #fix column name

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Males_new$TotalDistance.CP.cm) #make sure to change selected column
colnames(dataframe_combine)[5] <- "Value" #Fix name of individual data point column
dataframe_combine <- dataframe_combine[-2] #Remove extra treatment column

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev #upper error
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev #lower error

#Make Graph#
png("OF_Male_DistanceTraveledofCenterPoint_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,5000)) +
  ggtitle("Males- Total Distance Moved") +
  ylab(expression("Total Distance Moved in 10 Minutes (cm)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Male Distance Moved, echo = FALSE}
print(p)
```

## Females- Distance Moved
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Females_new$TotalDistance.CP.cm, as.character(Females_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Females_new$TotalDistance.CP.cm, as.character(Females_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Females_new$TotalDistance.CP.cm) #change column
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("OF_Female_DistanceTraveledofCenterPoint_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,5000)) +
  ggtitle("Females- Total Distance Moved") +
  ylab(expression("Total Distance Moved in 10 Minutes (cm)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Female Distance Moved, echo = FALSE}
print(p)
```

# Percent in Center

## Males- Percent in Center
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Males_new$Percent.Inside, as.character(Males_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints) 
colnames(Mean)[1] <- "Mean" 

Stdev <- tapply(Males_new$Percent.Inside, as.character(Males_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Males_new$Percent.Inside) #change column
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("OF_Male_PercentTimeCenter_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Males- Percent Time Spent in Center") +
  ylab(expression("Percent Time in Center (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Male Percent Time in Center, echo = FALSE}
print(p)
```

## Females- Percent in Center
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Females_new$Percent.Inside, as.character(Females_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints) 
colnames(Mean)[1] <- "Mean" 

Stdev <- tapply(Females_new$Percent.Inside, as.character(Females_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Females_new$Percent.Inside) #change column
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("OF_Female_PercentTimeCenter_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Females- Percent Time Spent in Center") +
  ylab(expression("Percent Time in Center (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Female Percent Time in Center, echo = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```