---
title: "P50 Offspring Brain Weights, AIN-76A diet with MD or Alcohol and Iron Supplement or Water"
author: "Kaylee Helfrich"
date: "2/12/2021"
output: 
  pdf_document: default
  html_document: default
data: "Offspring_Organ_Weights_P50_CLEAN.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/P22P50BrainWeights")
options(tinytex.verbose = TRUE)
```

# Graphing P50 Brain Weights
This document details my graphing of the brain weights on P50 from the postnatal portion of the rat study. This data includes all animals that were collected at P50. The graphs include left and right brain weights (and cerebrum weight), cerebellum weight, total brain weight, and body weight to brain ratio. All data within this analysis was collected by Kaylee Helfrich and Rachel Hodges.
The study design was as follows. Dams were Long-Evans rats that were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5 and also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use 2-way ANOVA to assign significance to the measures (alcohol vs. MD, iron vs. water). 

# Importing Files and Arranging Data
```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/P22P50BrainWeights")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "Offspring_Organ_Weights_P50_CLEAN.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("CON", "CON+Iron","PAE", "PAE+Iron")
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

## Males- Equalize Row Number by Exposure
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Males %>% count(Exposure) #Calculate how many individual Males there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Exposure <- ActualGroupOrder #add new column so that # of points to be added is assigned to exposure
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
MDH2O <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
MDFe <- DiffPoints[2,1]
AlcH2O <- DiffPoints[3,1]
AlcFe <- DiffPoints[4,1] 

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 14)) #create an empty dataframe filled with NA's
vector <- rep(c("CON", "CON+Iron", "PAE", "PAE+Iron"), times = c(MDH2O, MDFe, AlcH2O, AlcFe)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Exposure <- vector #add in the Exposure column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1,15,2:14)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Males)) #set the names of the new df to match the original df
Males_new <- rbind(Males, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Males_new %>% count(Exposure)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Males_new <- Males_new[order(Males_new$Exposure), ]
Male_NumPoints <- NumPoints
```
### Number of Missing Points to Expect in Male Graphs
```{r echo = FALSE}
print(Nrow)
```

## Females- Equalize Row Number by Exposure
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Females %>% count(Exposure) #Calculate how many individual Females there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Exposure <- ActualGroupOrder #add new column so that # of points to be added is assigned to exposure
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
MDH2O <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
MDFe <- DiffPoints[2,1]
AlcH2O <- DiffPoints[3,1]
AlcFe <- DiffPoints[4,1] 

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 14)) #create an empty dataframe filled with NA's
vector <- rep(c("CON", "CON+Iron", "PAE", "PAE+Iron"), times = c(MDH2O, MDFe, AlcH2O, AlcFe)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Exposure <- vector #add in the Exposure column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1,15,2:14)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Females)) #set the names of the new df to match the original df
Females_new <- rbind(Females, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Females_new %>% count(Exposure)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Females_new <- Females_new[order(Females_new$Exposure), ]
Female_NumPoints <- NumPoints
```
### Number of Missing Points to Expect in Female Graphs
```{r echo = FALSE}
print(Nrow)
```

# Total Brain  Weight 

## Total Brain  Weight in Males
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Males_new$Total.Brain.Weight , as.character(Males_new$Exposure), mean, na.rm=TRUE)
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Males_new$Total.Brain.Weight, as.character(Males_new$Exposure), sd, na.rm=TRUE)
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Males_new$Total.Brain.Weight)
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("P50_TotalBrainWtMales_AllData_PAExFe_Dotplot_ForPres.png", units="in", width=4, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "#BDB8AD",
                             "PAE" = "#EBE7E0",
                             "CON+Iron" = "#44749D",
                             "PAE+Iron" = "#C6D4E1"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,2.6)) +
  #ggtitle("P50- Total Brain Weight- Males") +
  ylab(expression("Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 28),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=24, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=24,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r P50 Male Total Brain Weight, echo = FALSE}
print(p)
```

## Total Brain  Weight in Females
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Females_new$Total.Brain.Weight, as.character(Females_new$Exposure), mean, na.rm=TRUE) 
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints)) 
Mean$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Females_new$Total.Brain.Weight, as.character(Females_new$Exposure), sd, na.rm=TRUE) 
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints)) 
Stdev$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints) 
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, Females_new$Total.Brain.Weight) 
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev 
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("P50_TotalBrainWtFemales_AllData_PAExFe_Dotplot_ForPres.png", units="in", width=4, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "#BDB8AD",
                             "PAE" = "#EBE7E0",
                             "CON+Iron" = "#44749D",
                             "PAE+Iron" = "#C6D4E1"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,2.6)) +
  #ggtitle("P50- Total Brain Weight- Females") +
  ylab(expression("Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 28),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=24, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=24,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r P50 Female Total Brain Weight, echo = FALSE}
print(p)
```

# Brain to Body Weight Ratio 

## Brain to Body Weight Ratio in Males
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Males_new$Brain.to.Body.Weight.Ratio , as.character(Males_new$Exposure), mean, na.rm=TRUE)
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Males_new$Brain.to.Body.Weight.Ratio, as.character(Males_new$Exposure), sd, na.rm=TRUE)
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Males_new$Brain.to.Body.Weight.Ratio)
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("P50_BraintoBodyRatioMales_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.011)) +
  ggtitle("P50- Brain to Body Weight Ratio- Males") +
  ylab(expression("Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r P50 Male Brain to Body Weight Ratio, echo = FALSE}
print(p)
```

## Brain to Body Weight Ratio in Females
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Females_new$Brain.to.Body.Weight.Ratio, as.character(Females_new$Exposure), mean, na.rm=TRUE) 
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints)) 
Mean$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Females_new$Brain.to.Body.Weight.Ratio, as.character(Females_new$Exposure), sd, na.rm=TRUE) 
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints)) 
Stdev$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints) 
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, Females_new$Brain.to.Body.Weight.Ratio) 
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev 
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("P50_BraintoBodyWeightRatioFemales_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.011)) +
  ggtitle("P50- Brain to Body Weight Ratio- Females") +
  ylab(expression("Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r P50 Female Brain to Body Weight Ratio, echo = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```