---
title: "T-maze Learning and Memory"
author: "Kaylee Helfrich"
date: "5/29/2020-2/22/2021"
output:
  pdf_document: default
  html_document: default
data: "T-maze_AllData.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/T-maze")
options(tinytex.verbose = TRUE)
```

# Introduction
This graph shows T-maze data from the rat offspring used for behavior testing. The four exposure groups are maltodextrin (MD), prenatal alcohol exposure (PAE), MD+iron, and PAE+iron. These were generated using the standard rat model (PAE or MD at 5g/kg split dose from GD13.5-19.5, and iron dosed at 6mg/kg from GD12.5-19.5). Data are separated into male and female. These graphs display the data in a few different ways, such as line graphs to show learning across the training sessions and boxplots to show data on Sessions to criterion and memory at the 30s and 60s time delays. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron2/T-maze")
library(ggplot2)
library(plotrix)
library(dplyr)
library(tidyverse)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by Exposure to be alphabetical}
File <- "Tmaze_AllData.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Exposure), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r}
ActualGroupOrder <- c("CON", "CON+Iron", "PAE", "PAE+Iron")
```

## Create separate males and females tables
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ]
Females <- data_frame[ which(data_frame$Sex=='F'), ]
```

# Create line graphs for the learning sessions
This shows how the rats learn, moving from 50% correct to near-100% correct.  

## Create mean and standard deviation table for males
```{r}
#Session 1
Males.1 <- tapply(Males$Training.1, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.1 <- as.data.frame(Males.1)
Males.1$Exposure <- ActualGroupOrder
colnames(Males.1)[1] <- "Mean" #fix column name
Males.stdev.1 <- tapply(Males$Training.1, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.1$Stdev <- Males.stdev.1
Males.1$Session <- rep("1", 4)

#Session 2
Males.2 <- tapply(Males$Training.2, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.2 <- as.data.frame(Males.2)
Males.2$Exposure <- ActualGroupOrder
colnames(Males.2)[1] <- "Mean" #fix column name
Males.stdev.2 <- tapply(Males$Training.2, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.2$Stdev <- Males.stdev.2
Males.2$Session <- rep("2", 4)

#Session 3
Males.3 <- tapply(Males$Training.3, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.3 <- as.data.frame(Males.3)
Males.3$Exposure <- ActualGroupOrder
colnames(Males.3)[1] <- "Mean" #fix column name
Males.stdev.3 <- tapply(Males$Training.3, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.3$Stdev <- Males.stdev.3
Males.3$Session <- rep("3", 4)

#Session 4
Males.4 <- tapply(Males$Training.4, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.4 <- as.data.frame(Males.4)
Males.4$Exposure <- ActualGroupOrder
colnames(Males.4)[1] <- "Mean" #fix column name
Males.stdev.4 <- tapply(Males$Training.4, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.4$Stdev <- Males.stdev.4
Males.4$Session <- rep("4", 4)

#Session 5
Males.5 <- tapply(Males$Training.5, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.5 <- as.data.frame(Males.5)
Males.5$Exposure <- ActualGroupOrder
colnames(Males.5)[1] <- "Mean" #fix column name
Males.stdev.5 <- tapply(Males$Training.5, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.5$Stdev <- Males.stdev.5
Males.5$Session <- rep("5", 4)

#Session 6
Males.6 <- tapply(Males$Training.6, as.character(Males$Exposure), mean, na.rm=TRUE)
Males.6 <- as.data.frame(Males.6)
Males.6$Exposure <- ActualGroupOrder
colnames(Males.6)[1] <- "Mean" #fix column name
Males.stdev.6 <- tapply(Males$Training.6, as.character(Males$Exposure), std.error, na.rm=TRUE)
Males.6$Stdev <- Males.stdev.6
Males.6$Session <- rep("6", 4)

#Merge all tables
Males_training_combined <- rbind(Males.1, Males.2, Males.3, Males.4, Males.5, Males.6)
Males_training_combined <- Males_training_combined[ ,c(2,1,3,4)]
Males_training_combined$Session <- as.numeric(as.vector(Males_training_combined$Session)) #convert "Session" to a numeric variable so the x-axis adjusts accordingly
names(Males_training_combined)[1] <- "Exposure"

#Adjust numbers to be a percent instead of a decimal
Males_training_combined$Mean <- Males_training_combined$Mean * 100
Males_training_combined$Stdev <- Males_training_combined$Stdev * 100

#Create error bar data
Males_training_combined$Upper <- Males_training_combined$Mean + Males_training_combined$Stdev
Males_training_combined$Lower <- Males_training_combined$Mean - Males_training_combined$Stdev

Males_training_combined$Exposure <- factor(Males_training_combined$Exposure, levels=c("CON", "PAE", "CON+Iron", "PAE+Iron"))
```

## Graph Male T-maze Learning- With Error Bars
```{r}
png("TmazeLearning_Males_StdError_PAExFe_Linegraph_B&W.png", units="in", width=8, height=6, res=600) 

males.training <- ggplot(data=Males_training_combined, aes(x=Session, y=Mean, group=Exposure)) +
  geom_point(aes(shape=Exposure)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure, color = Exposure)) +
  scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Male Learning Curve on the T-maze") +
  ylab(expression("% Correct Trials")) + 
  xlab(expression("Session Number")) +
  geom_hline(yintercept=50, linetype="dashed") +
  geom_hline(yintercept=75) +
  scale_color_manual(values=c("CON" = "#000000",
                             "PAE" = "#000000",
                             "CON+Iron" = "#000000",
                             "PAE+Iron" = "#000000"
                             )) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        axis.title.x = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9, family = "Times New Roman"),
        legend.title=element_text(family = "Times New Roman"), 
        legend.text=element_text(family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman"))
print(males.training)
dev.off() 
```
```{r Male Training With Error Bars, echo = FALSE}
print(males.training)
```

## Create mean and standard deviation table for females
```{r}
#Session 1
Females.1 <- tapply(Females$Training.1, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.1 <- as.data.frame(Females.1)
Females.1$Exposure <- ActualGroupOrder
colnames(Females.1)[1] <- "Mean" #fix column name
Females.stdev.1 <- tapply(Females$Training.1, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.1$Stdev <- Females.stdev.1
Females.1$Session <- rep("1", 4)

#Session 2
Females.2 <- tapply(Females$Training.2, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.2 <- as.data.frame(Females.2)
Females.2$Exposure <- ActualGroupOrder
colnames(Females.2)[1] <- "Mean" #fix column name
Females.stdev.2 <- tapply(Females$Training.2, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.2$Stdev <- Females.stdev.2
Females.2$Session <- rep("2", 4)

#Session 3
Females.3 <- tapply(Females$Training.3, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.3 <- as.data.frame(Females.3)
Females.3$Exposure <- ActualGroupOrder
colnames(Females.3)[1] <- "Mean" #fix column name
Females.stdev.3 <- tapply(Females$Training.3, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.3$Stdev <- Females.stdev.3
Females.3$Session <- rep("3", 4)

#Session 4
Females.4 <- tapply(Females$Training.4, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.4 <- as.data.frame(Females.4)
Females.4$Exposure <- ActualGroupOrder
colnames(Females.4)[1] <- "Mean" #fix column name
Females.stdev.4 <- tapply(Females$Training.4, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.4$Stdev <- Females.stdev.4
Females.4$Session <- rep("4", 4)

#Session 5
Females.5 <- tapply(Females$Training.5, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.5 <- as.data.frame(Females.5)
Females.5$Exposure <- ActualGroupOrder
colnames(Females.5)[1] <- "Mean" #fix column name
Females.stdev.5 <- tapply(Females$Training.5, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.5$Stdev <- Females.stdev.5
Females.5$Session <- rep("5", 4)

#Session 6
Females.6 <- tapply(Females$Training.6, as.character(Females$Exposure), mean, na.rm=TRUE)
Females.6 <- as.data.frame(Females.6)
Females.6$Exposure <- ActualGroupOrder
colnames(Females.6)[1] <- "Mean" #fix column name
Females.stdev.6 <- tapply(Females$Training.6, as.character(Females$Exposure), std.error, na.rm=TRUE)
Females.6$Stdev <- Females.stdev.6
Females.6$Session <- rep("6", 4)

#Merge all tables
Females_training_combined <- rbind(Females.1, Females.2, Females.3, Females.4, Females.5, Females.6)
Females_training_combined <- Females_training_combined[ ,c(2,1,3,4)]
Females_training_combined$Session <- as.numeric(as.vector(Females_training_combined$Session)) #convert "Session" to a numeric variable so the x-axis adjusts accordingly
names(Females_training_combined)[1] <- "Exposure"

#Adjust numbers to be a percent instead of a decimal
Females_training_combined$Mean <- Females_training_combined$Mean * 100
Females_training_combined$Stdev <- Females_training_combined$Stdev * 100

#Create error bar data
Females_training_combined$Upper <- Females_training_combined$Mean + Females_training_combined$Stdev
Females_training_combined$Lower <- Females_training_combined$Mean - Females_training_combined$Stdev

Females_training_combined$Exposure <- factor(Females_training_combined$Exposure, levels=c("CON", "PAE", "CON+Iron", "PAE+Iron"))
```

## Graph Female T-maze Learning- with Error Bars
```{r}
png("TmazeLearning_Females_StdError_PAExFe_Linegraph_B&W.png", units="in", width=8, height=6, res=600) 

females.training <- ggplot(data=Females_training_combined, aes(x=Session, y=Mean, group=Exposure)) +
  geom_point(aes(shape=Exposure)) +
  scale_shape_manual(values=c(15, 17, 18, 19)) +
  geom_line(aes(linetype=Exposure, color = Exposure)) +
  scale_linetype_manual(values=c("solid", "longdash", "dotted", "twodash")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+Iron", "PAE+Iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Female Learning Curve on the T-maze") +
  ylab(expression("% Correct Trials")) + 
  xlab(expression("Session Number")) +
  geom_hline(yintercept=50, linetype="dashed") +
  geom_hline(yintercept=75) +
  scale_color_manual(values=c("CON" = "#000000",
                             "PAE" = "#000000",
                             "CON+Iron" = "#000000",
                             "PAE+Iron" = "#000000"
                             )) +
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        legend.key=element_blank(), 
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        axis.title.x = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9, family = "Times New Roman"),
        legend.title=element_text(family = "Times New Roman"), 
        legend.text=element_text(family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman"))
print(females.training)
dev.off() 
```
```{r Female Training No Error Bars, echo = FALSE}
print(females.training)
```

### Males- Equalize Row Number by Exposure
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Males %>% count(Exposure) #Calculate how many individual Males there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Exposure <- ActualGroupOrder #add new column so that # of points to be added is assigned to exposure
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
MDH2O <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
MDFe <- DiffPoints[2,1]
AlcH2O <- DiffPoints[3,1]
AlcFe <- DiffPoints[4,1] 

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 19)) #create an empty dataframe filled with NA's
vector <- rep(c("CON", "CON+Iron", "PAE", "PAE+Iron"), times = c(MDH2O, MDFe, AlcH2O, AlcFe)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Exposure <- vector #add in the Exposure column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1:4,20,5:19)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Males)) #set the names of the new df to match the original df
Males_new <- rbind(Males, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Males_new %>% count(Exposure)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Males_new <- Males_new[order(Males_new$Exposure), ]
Male_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Male Graphs
```{r echo = FALSE}
print(Nrow)
```

### Females- Equalize Row Number by Exposure
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Females %>% count(Exposure) #Calculate how many individual Females there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Exposure), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Exposure <- ActualGroupOrder #add new column so that # of points to be added is assigned to exposure
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
MDH2O <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
MDFe <- DiffPoints[2,1]
AlcH2O <- DiffPoints[3,1]
AlcFe <- DiffPoints[4,1] 

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 19)) #create an empty dataframe filled with NA's
vector <- rep(c("CON", "CON+Iron", "PAE", "PAE+Iron"), times = c(MDH2O, MDFe, AlcH2O, AlcFe)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Exposure <- vector #add in the Exposure column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1:4,20,5:19)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Females)) #set the names of the new df to match the original df
Females_new <- rbind(Females, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Females_new %>% count(Exposure)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Females_new <- Females_new[order(Females_new$Exposure), ]
Female_NumPoints <- NumPoints
```
#### Number of Missing Points to Expect in Female Graphs
```{r echo = FALSE}
print(Nrow)
```

# Remaking 30s Delay Data as Barplots
## Males 30s Delay
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Males_new$X30s.Delay, as.character(Males_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Males_new$X30s.Delay, as.character(Males_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Males_new$X30s.Delay) #change column
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine$Value <- dataframe_combine$Value * 100
dataframe_combine$Mean <- dataframe_combine$Mean * 100
dataframe_combine$Upper <- dataframe_combine$Upper * 100
dataframe_combine$Lower <- dataframe_combine$Lower * 100

#Make Graph#
png("Tmaze_Male_30sDelay_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.25, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105)) +
  ggtitle("Males- Percent Correct Trials with 30s Delay") +
  ylab(expression("Correct Trials (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Male Percent Correct Trials 30s Delay Barplot, echo = FALSE}
print(p)
```

## Females Sessions to Criterion
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Females_new$X30s.Delay, as.character(Females_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Females_new$X30s.Delay, as.character(Females_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Females_new$X30s.Delay) #change column
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine$Value <- dataframe_combine$Value * 100
dataframe_combine$Mean <- dataframe_combine$Mean * 100
dataframe_combine$Upper <- dataframe_combine$Upper * 100
dataframe_combine$Lower <- dataframe_combine$Lower * 100

#Make Graph#
png("Tmaze_Female_30sDelay_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.25, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105)) +
  ggtitle("Females- Percent Correct Trials with 30s Delay") +
  ylab(expression("Correct Trials (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Female Percent Correct Trials 30s Delay Barplot, echo = FALSE}
print(p)
```

# Remaking 60s Delay Data as Barplots
## Males 60s Delay
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Males_new$X60s.Delay, as.character(Males_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Male_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Males_new$X60s.Delay, as.character(Males_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Male_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Male_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Males_new$X60s.Delay) #change column
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine$Value <- dataframe_combine$Value * 100
dataframe_combine$Mean <- dataframe_combine$Mean * 100
dataframe_combine$Upper <- dataframe_combine$Upper * 100
dataframe_combine$Lower <- dataframe_combine$Lower * 100

#Make Graph#
png("Tmaze_Male_60sDelay_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.25, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105)) +
  ggtitle("Males- Percent Correct Trials with 60s Delay") +
  ylab(expression("Correct Trials (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Male Percent Correct Trials 60s Delay Barplot, echo = FALSE}
print(p)
```

## Females Trials to Criterion
```{r, echo = FALSE, warning = FALSE, message = FALSE}
Mean <- tapply(Females_new$X60s.Delay, as.character(Females_new$Exposure), mean, na.rm=TRUE) #change column
Mean <- as.data.frame(rep(Mean, each = Female_NumPoints))
Mean$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(Females_new$X60s.Delay, as.character(Females_new$Exposure), sd, na.rm=TRUE) #change column
Stdev <- as.data.frame(rep(Stdev, each = Female_NumPoints))
Stdev$Exposure <- rep(ActualGroupOrder, each = Female_NumPoints)
colnames(Stdev)[1] <- "Stdev"

dataframe_combine <- cbind(Mean, Stdev, Females_new$X60s.Delay) #change column
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

dataframe_combine$Value <- dataframe_combine$Value * 100
dataframe_combine$Mean <- dataframe_combine$Mean * 100
dataframe_combine$Upper <- dataframe_combine$Upper * 100
dataframe_combine$Lower <- dataframe_combine$Lower * 100

#Make Graph#
png("Tmaze_Female_60sDelay_AllData_PAExFe_Dotplot_B&W.png", units="in", width=7, height=7, res=600) 

sets <- c("CON", "PAE", "CON+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Exposure, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Exposure),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "PAE" = "grey51",
                             "CON+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Exposure, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.25, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,105)) +
  ggtitle("Females- Percent Correct Trials with 60s Delay") +
  ylab(expression("Correct Trials (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=20, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=20,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Female Percent Correct Trials 60s Delay Barplot, echo = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```